---
title: "ADA_results"
output: html_document
date: "2024-01-08"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
install.packages("readxl")
install.packages("stringr")
```

#load packages 
```{r}
library(tmap)
library(ozmaps)
library(tidyverse)
library(here)
library(sf)
library(ggplot2)
library(dplyr)
library(tmaptools)
library(gridExtra)
library(cowplot)
library(mapview)
library(leaflet)
library(readxl)
library(stringr)
```
#load datasets of ADAs

```{r}
ADA_01_affected<-st_read(here("output_data/Prop_affected_area_ADA1.shp"))
ADA_02_affected<-st_read(here("output_data/Prop_affected_area_ADA2.shp"))
ADA_03_affected<-st_read(here("output_data/Prop_affected_area_ADA3.shp"))
ADA_04_affected<-st_read(here("output_data/Prop_affected_area_ADA4.shp"))
ADA_05_affected<-st_read(here("output_data/Prop_affected_area_ADA5.shp"))
ADA_06_affected<-st_read(here("output_data/Prop_affected_area_ADA6.shp"))
ADA_07_affected<-st_read(here("output_data/Prop_affected_area_ADA7.shp"))
ADA_08_affected<-st_read(here("output_data/Prop_affected_area_ADA8.shp"))
```

#create a new column in each with the percentage of area exposed to SLR in 2100 and another one for the ADA number

#adding columns we will need to ADAs risk result
```{r}
ADA_01_exposurepercentage<-ADA_01_affected%>%
  mutate(
    percentage= affct__*100,
    ADA = 01
    )
ADA_02_exposurepercentage<-ADA_02_affected%>%
  mutate(
    percentage= affct__*100,
    ADA = 02
    )
ADA_03_exposurepercentage<-ADA_03_affected%>%
 mutate(
    percentage= affct__*100,
    ADA = 03
    )
ADA_04_exposurepercentage<-ADA_04_affected%>%
  mutate(
    percentage= affct__*100,
    ADA = 04
    )
ADA_05_exposurepercentage<-ADA_05_affected%>%
  mutate(
    percentage= affct__*100,
    ADA = 05
    )
ADA_06_exposurepercentage<-ADA_06_affected%>%
 mutate(
    percentage= affct__*100,
    ADA = 06
    )
ADA_07_exposurepercentage<-ADA_07_affected%>%
  mutate(
    percentage= affct__*100,
    ADA = 07
    )
ADA_08_exposurepercentage<-ADA_08_affected%>%
  mutate(
    percentage= affct__*100,
    ADA = 08
    )
```


#bind datasets of ADAs
```{r}
all_ADAs_exposure<-bind_rows(ADA_01_exposurepercentage, ADA_02_exposurepercentage, ADA_03_exposurepercentage, ADA_04_exposurepercentage, ADA_05_exposurepercentage, ADA_06_exposurepercentage, ADA_07_exposurepercentage, ADA_08_exposurepercentage)
```

```{r}
all_ADAs_exposure<-all_ADAs_exposure%>%
  select(-diss, -diss2, -diss_1, -diss2_1, area_m2, affc__2,   affct__, percentage, ADA, geometry )
```
```{r}
all_ADAs_exposure_LGA<- st_intersection(all_ADAs_exposure, LGA_reproj)
```

#map of Australia

```{r}
QLD_map<st_read(here("output_data/QLD_map.shp"))
```


#plot result of the percentage in a map
# for ADAs- change color?

```{r}
tmap_mode("view")
tm_shape(QLD_map) +
  tm_polygons(col= "lightgrey", alpha=0.2)+
tm_shape(all_ADAs_exposure) +
tm_bubbles(size = "percentage", col = "red")
```
#tm_bubbles
```{r}
tmap_mode("view")+
tm_shape(QLD_map) +
  tm_polygons(col= "lightgrey", alpha=0.2)+
tm_shape(shp = all_ADAs_exposure) +
tm_bubbles(size = "percentage")
```

```{r}
tmap_mode("view")+
tm_shape(shp = all_ADAs_exposure) +
tm_bubbles(size = "percentage", auto.palette.mapping = TRUE, contrast = 1, max.categories = 12)
```

#I want this to come up too (shp = SLR_projection_QLD_reproj)+
#different colors each break or something like that (bubbles)
#polygons try with them with different colors

```{r}
tmap_mode("plot")+
 tm_shape(QLD_map) +
  tm_polygons(col= "lightgrey", alpha=0.2)+
  tm_shape(shp = all_ADAs_exposure) +
tm_bubbles(size = 0.3, 
            col = "percentage",
            title.col = "% of each ADA expected to be exposed by SLR",
           palette = viridis(10),
           style= "quantile")+
tm_layout(title= 'Hotspots of risk to ADAs in QLD',             
          title.position = c("right", "top"),
          legend.position = c("right", "top"),
   inner.margins = c(0.1, 0.1, 0.1, 0.3))
```


```{r}
tmap_mode("plot")+
 tm_shape(QLD_map) +
  tm_polygons(col= "lightgrey", alpha=0.2)+
  tm_shape(shp = all_ADAs_exposure) +
tm_bubbles(size = 0.3, 
            col = "percentage",
            title.col = "% of each ADA expected to be exposed by SLR",
           palette = viridis(10),
           style= "quantile")+
tm_layout(legend.position = c("right", "top"),
   inner.margins = c(0.1, 0.1, 0.1, 0.3))

```


#Caitie thinks I could have the polygons instead of bubbles coloured by their exposure 

```{r}
tmap_mode("view")+
tm_shape(shp = all_ADAs_exposure) +
tm_polygons(col = "percentage",
           style= "quantile",
           palette = '-YlGn',
           border.alpha =0.6 )
```

```{r}
ADAs_4plot<- read_excel(here("raw_data/ADAs result_4plots.xlsx"))
```


#this is a possibility

```{r}
ggplot(data = all_ADAs_exposure, aes(y =percentage, x =  area_m2)) +
  geom_point() +
  xlab("percentage of the area exposed") +
  ylab("Area") +
  theme_bw()

```

#another 
```{r}
ggplot(data = all_ADAs_exposure, aes(y =percentage, x =  area_m2)) +
  geom_point() +
  xlab("percentage of the area exposed") +
  ylab("Area") +
  theme_bw()
#put color possibility of pallete here if I can 

```
 
 
#this is a possibility but coloured would look better
```{r}
area_median<-median(all_ADAs_exposure$area_m2)
prop_median<-median(all_ADAs_exposure$affc__2)

ggplot(data = all_ADAs_exposure, aes(y = area_m2, x = percentage)) +
geom_point() +
xlab("Prop. area affected") +
ylab("Area") +
theme_bw() +
geom_hline(yintercept = area_median) 
geom_vline(xintercept = prop_median)
```
```{r}
tmap_mode("plot")+
tm_shape(shp = all_ADAs_exposure) +
tm_polygons(col = "percentage",
           style= "quantile",
           palette = '-viridis',
           border.alpha =1 )
```
```{r}
tmap_mode("plot")+
  tm_shape(QLD_map) +
  tm_polygons(col= "lightgrey", alpha=0.2)+
  tm_polygons()+
  tm_shape(shp = all_ADAs_exposure) +
  tm_polygons(col = "percentage",
           style= "quantile",
           palette = 'viridis',
           border.alpha =0.2 )
```
```{r}
ggplot() +
  geom_sf(data = QLD_map, fill = "gray", alpha = 0.2) +  # Base map with QLD_map
  geom_point(data = all_ADAs_exposure, aes(geometry = geometry, color = percentage), 
             alpha = 0.8, stat = "sf_coordinates") +  # Bubbles with color mapped
  scale_size_continuous(range = c(1, 10)) +  # Adjust the size range of the bubbles
  scale_color_viridis_c(name = "Percentage of the ADA exposed by 2100", option = "viridis") +  # Color scale with viridis palette and title
  theme_minimal() +  # Minimal theme for better visualization
  theme(
    legend.position =  "bottom",  # Adjust legend position
    legend.title = element_text(size = 12),  # Adjust legend title size
    plot.margin = margin(10, 30, 10, 10)  # Adjust plot margins
  ) +
  labs(x = "Longitude", y = "Latitude")  # Add labels to the x and y axes

```
```{r}
ggplot() +
  geom_sf(data = QLD_map, fill = "gray", alpha = 0.2) +  # Base map with QLD_map
  geom_point(data = all_ADAs_exposure, aes(geometry = geometry, color = percentage), 
             alpha = 0.8, stat = "sf_coordinates") +  # Bubbles with color mapped
  scale_size_continuous(range = c(1, 10)) +  # Adjust the size range of the bubbles
  scale_color_viridis_c(name = "Percentage of the ADA exposed by 2100", option = "plasma") +  # Color scale with viridis palette and title
  theme_minimal() +  # Minimal theme for better visualization
  theme(
    legend.position =  "bottom",  # Adjust legend position
    legend.title = element_text(size = 10),  # Adjust legend title size
    plot.margin = margin(10, 30, 10, 10)  # Adjust plot margins
  ) +
  labs(x = "Longitude", y = "Latitude")  # Add labels to the x and y axes

```

```{r}
ADA_results_map<-ggplot() +
  geom_sf(data = QLD_map, fill = "gray", alpha = 0.2) +  # Base map with QLD_map
  geom_point(data = all_ADAs_exposure, aes(geometry = geometry, color = percentage), 
             alpha = 0.8, stat = "sf_coordinates") +  # Bubbles with color mapped
  scale_size_continuous(range = c(1, 10)) +  # Adjust the size range of the bubbles
  scale_color_viridis_c(name = "Sea level rise \nexposure (%)", option = "plasma") +  # Color scale with viridis palette and title
  theme_minimal() +  # Minimal theme for better visualization
  theme(
    legend.position =  "right",  # Adjust legend position
    legend.title = element_text(size = 10),  # Adjust legend title size
    plot.margin = margin(10, 30, 10, 10)  # Adjust plot margins
  ) +
  labs(x = "Longitude", y = "Latitude")  # Add labels to the x and y axes

```
```{r}
plot(ADA_results_map)
```

#bar plot for ADAs

```{r}
# Create a bar plot
ADA_bar<-ggplot(all_ADAs_exposure_LGA, aes(x = reorder(ADA, -percentage), y = affct__,  fill = percentage)) +
  geom_bar(stat = "identity") +
  coord_flip() +  # Flip the axis for better readability
  labs(x = "ADA", y = "proportion of exposed area within ADA to SLR by 2100") +
   scale_fill_viridis_c(option = "plasma", name = "Proportion of  \n ADA exposed") +
  theme_minimal()

```
```{r}
plot(ADA_bar)
```

```{r}
# Create a bar plot with LGA labels
ggplot(all_ADAs_exposure_LGA, aes(x = reorder(ADA, -percentage), y = affct__, fill = percentage)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = LGA), hjust = 0.1, size = 3) +  # Add LGA labels just outside the bars
  coord_flip() +  # Flip the axis for better readability
  labs(x = "ADA", y = "Proportion of exposed area within ADA to SLR by 2100") +
  scale_fill_viridis_c(option = "plasma", name = "Proportion of \n ADA exposed") +
  theme_minimal()

```


