---
title: "Plot NSW Aquaculture"
output: html_document
date: "2023-05-22"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(mapview)
library(tidyverse)
library(ozmaps)
library(here)
library(tmap)
library(sf)
```

# NSW aquaculture

This data is from: URL
e-mail that was sent from fisheries.data@dpi.nsw.gov.au
I downloaded this on: 18/may/2023

Data Licensing:
This downloadable data is licensed under a Creative Commons Attribution - 4.0 International License (CC BY 4.0). Full credit must be given to NSW Department of Primary Industries.

```{r}
nsw<-st_read(here("raw_data/NSW_aqua/Aquaculture_Leases.shp")) # Reading in NSW aquaculture data
```

```{r}
plot(st_geometry(nsw))
```

```{r}
mapview(ozmap_states) +
  mapview(nsw)
```
# Australia ShP map
This data is from: https://www.abs.gov.au/statistics/standards/australian-statistical-geography-standard-asgs-edition-3/jul2021-jun2026/access-and-downloads/digital-boundary-files  
Australia - 2021 - Shapefile
States and Territories - 2021 - Shapefile

I downloaded this on: 23/May/2023

```{r}
australia<-st_read(here("raw_data/Australia_country_SHP/AUS_2021_AUST_GDA2020.shp")) 
```
```{r}
plot(st_geometry(australia))
```


