---
title: "Sticking_files_gee_output"
output: html_document
date: "2024-03-18"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(sf)
library(tidyverse)
library(here)
library(tmap)
library(dplyr)
```

#stick all the shapefiles from the GEE output 

#worked properly from here to combined
#call folder with files
#NDWI_p_80
```{r}
shp_files<-list.files(here("D:/Documents_HD/QLD_SLR_Aquaculture/output_data/GEE_shp_20_21/NDWI_p80"), pattern = "NDWI_p80", full.names = TRUE)
```

#separate in the folder the files with different endings that arent .shp
```{r}
shp_filesdbf<-shp_files[grep(shp_files, pattern = ".dbf")]
shp_filesprj<-shp_files[grep(shp_files, pattern = ".prj")]
shp_filesshx<-shp_files[grep(shp_files, pattern = ".shx")]
```

#make lists subtracting from those done above
```{r}
shp_fileswithoutdbf<-shp_files[!shp_files %in% shp_filesdbf]
shp_fileswithoutdbfprj<-shp_fileswithoutdbf[!shp_fileswithoutdbf %in% shp_filesprj]
shp_fileswithoutdbfprjshx<- shp_fileswithoutdbfprj[!shp_fileswithoutdbfprj %in% shp_filesshx]
```

#generate a list 
```{r}
shapes<-list()
```


#read all the shapefiles in a loop
```{r}
for (n in 1:length(shp_fileswithoutdbfprjshx)) {
  shapes[[n]] <- st_read(shp_fileswithoutdbfprjshx[n])}
 
if (length(shp_fileswithoutdbfprjshx) == 0) {
  stop("No shapefiles found in the folder.")
}
```

#combined all 37 shapefiles
```{r}
combined_shapefile <- bind_rows(shapes)
```

#save the combined shapefile
```{r}
st_write(combined_shapefile, here("output_data/QLD_aqua_ponds_combined_shapefile.shp"), delete_layer = TRUE)
```

#NOW DO THE SAME FOR THE OTHER SHAPEFILES

#NDWI P20
#worked properly from here to combined
#call folder with files
```{r}
shp_files<-list.files(here("D:/Documents_HD/QLD_SLR_Aquaculture/output_data/GEE_shp_20_21/NDWI_p20"), pattern = "NDWI_p20", full.names = TRUE)
```

#separate in the folder the files with different endings that arent .shp
```{r}
shp_filesdbf<-shp_files[grep(shp_files, pattern = ".dbf")]
shp_filesprj<-shp_files[grep(shp_files, pattern = ".prj")]
shp_filesshx<-shp_files[grep(shp_files, pattern = ".shx")]
```

#make lists subtracting from those done above
```{r}
shp_fileswithoutdbf<-shp_files[!shp_files %in% shp_filesdbf]
shp_fileswithoutdbfprj<-shp_fileswithoutdbf[!shp_fileswithoutdbf %in% shp_filesprj]
shp_fileswithoutdbfprjshx<- shp_fileswithoutdbfprj[!shp_fileswithoutdbfprj %in% shp_filesshx]
```

#generate a list 
```{r}
shapes<-list()
```

#read all the shapefiles in a loop
```{r}
for (n in 1:length(shp_fileswithoutdbfprjshx)) {
  shapes[[n]] <- st_read(shp_fileswithoutdbfprjshx[n])}
 
if (length(shp_fileswithoutdbfprjshx) == 0) {
  stop("No shapefiles found in the folder.")
}
```

#combined all shapefiles in one 
```{r}
combined_shapefile_NDWI_p20 <- bind_rows(shapes)
```

#save the combined shapefile
```{r}
st_write(combined_shapefile_NDWI_p20, here("output_data/QLD_aqua_ponds_combined_shapefile_NDWI_p20.shp"), delete_layer = TRUE)
```
#in case I want to combine both Shapefiles I could
```{r}
combined_shapefile_NDWI_p20_p80 <- bind_rows(combined_shapefile_NDWI_p20, QLD_ponds_GEEOutput)
```

```{r}
qtm(combined_shapefile_NDWI_p20_p80)
```
```{r}
#tmap_mode("view")
tm_shape((combined_shapefile_NDWI_p20))+
tm_polygons(col="yellow")+ 
tm_shape((QLD_ponds_GEEOutput))+
tm_polygons(col="blue")+
   tm_basemap(providers$Esri.WorldImagery)
  
```


