---
title: "ImpactSLR_Erosion_over_aquaculture"
output: html_document
date: "august 2024"
---

#load packages I will need
```{r}
library(tidyverse)
library(here)
library(tmap)
library(sf)
library(ggplot2)
library(dplyr)
```

# load data
#Queensland leases data obtained from DAF and then ground truthed in the seascapes Lab

```{r}
qld_leases<-st_read(here("output_data/RESULTS/Final_species2024_leases.gpkg"))
```

#reproject data of the queensland aquaculture leases and create a new column with the area of the polygons
```{r}
Final_species2024_leases_productive<-Final_species2024_leases%>%
  filter(Aqcltr_=="Y")
```

```{r}
qld_leases_reproj<-st_transform(qld_leases, 3577)
```

#load australia map
```{r}
Australia_map<- st_read(here("raw_data/Australia_country_SHP/AUS_2021_AUST_GDA2020.shp"))
```

#load data 
#Queensland state map

```{r}
Qld_map<-st_read(here("output_data/QLD_map.shp"))
```

#load data 
#Queensland erosion all components erosion and sLR obtained http://qldspatial.information.qld.gov.au/catalogue/custom/search.page?q=%22Erosion prone area all components%22


```{r}
QLD_coastal_erosion<-st_read(here("raw_data/QSC_all_components_of_SLR/Erosion_prone_area_all_components.shp"))
```

# reproject all data previously uploaded in shapefile (to 3577 -Australian Albers)

```{r}
Qld_reproj<-st_transform(Qld_map, 3577)

Australia_map_reproj<-st_transform(Australia_map, 3577)

QLD_coastal_erosion_reproj<-st_transform(QLD_coastal_erosion, 3577)
```

# Dissolve coastal erosion all components layer
```{r}
QLD_coastal_erosion_allcomp_diss<-QLD_coastal_erosion_reproj %>%
  mutate(diss = 1) %>% #create column to dissolve by
  group_by(diss) %>% #group by column you created
  summarise(diss2 = sum(diss, na.rm = T)) #combine column into one new variable

```

#intersect  aquaculture leases with dissolved coastal erosion  layer

```{r}

qld_leases_erosion<-st_intersection(QLD_coastal_erosion_allcomp_diss, qld_leases)

```
#only the yes column before intersection (yes that were ground truthed as aquaculture)
```{r}

qld_leases_erosion_productiveGT<-st_intersection(QLD_coastal_erosion_allcomp_diss, Final_species2024_leases_productive)

```
#this shows the erosion over the ponds foud in the leases GEE found were productive 
```{r}

qld_leases_erosion_productiveGEE<-st_intersection(QLD_coastal_erosion_allcomp_diss, QLD_ponds_in_leases)
```

#The final productive farms were the ones with ponds called : spatial_leases_with_ponds so this shows which ones of them are exposed to SLR
```{r}
Exposed_leases_with_ponds_GEE<-st_intersection(QLD_coastal_erosion_allcomp_diss, spatial_leases_with_ponds)
```


#Create a Column and get the proportion of each lease that might be affected following erosion and SLR in 2100 in QLD
```{r}
qld_leases_erosion <- qld_leases_erosion %>%
  mutate(affected_area_m2 = as.numeric(st_area(.)),
         propaffectedArea= affected_area_m2/lease_area_m2)
```
```{r}
qld_leases_erosion_productiveGT <- qld_leases_erosion_productiveGT %>%
  mutate(affected_area_m2 = as.numeric(st_area(.)),
         propaffectedArea= affected_area_m2/lease_area_m2)
```
```{r}
qld_leases_erosion_productiveGEE <- qld_leases_erosion_productiveGEE %>%
  mutate(affected_area_m2 = as.numeric(st_area(.)),
         propaffectedArea= affected_area_m2/lease_area_m2)
```

```{r}
Exposed_leases_with_ponds_GEE<-Exposed_leases_with_ponds_GEE%>%
  mutate(affected_area_km2 = as.numeric(st_area(.)),
         propaffectedArea= affected_area_km2/lease_area_km2)

```



#Create a shapefile of the intersection between the Aquaculture leases in Queensland and erosion prone areas in Queensland to check how many of them would be potetially affected
```{r}
st_write(qld_leases_erosion, here("output_data/RESULTS/qld_leases_erosion.shp"), delete_layer = TRUE)
```
```{r}
st_write(qld_leases_erosion_productiveGT, here("output_data/RESULTS/qld_leases_erosion_productiveGT.shp"), delete_layer = TRUE)
```
```{r}
st_write(qld_leases_erosion_productiveGEE, here("output_data/RESULTS/qld_leases_erosion_productiveGEE.shp"), delete_layer = TRUE)
```


#dissolving by farm ID (grouped) or without doubles

```{r}
totalleasesaffected<- qld_leases_erosion%>% 
  group_by(qldglb_)%>%
  summarise(geometry= st_union(geometry))
```

#species check  all leases before erosion
```{r}
prawn_leases<-qld_leases%>%
   filter(grepl('Prawn', Species))
barramundi_leases<-qld_leases%>%
  filter(grepl('Barra', Species))
Redclaw_leases<-qld_leases%>%
  filter(grepl('Red', Species))
Freshwater_fish_leases<-qld_leases%>%
   filter(grepl('Freshwater fish', Species))
Hatchery_leases<-qld_leases%>%
  filter(grepl('Hatchery', Species))
Ornamental_leases<-qld_leases%>%
  filter(grepl('Orna', Species))
```


#  histograms building for leases results

```{r}
ggplot(qld_leases_erosion) +
  aes(propaffectedArea, fill = Species
      ) +
  geom_histogram() +
  theme_classic() +
  scale_fill_viridis_d() +
  labs(x = "Prop. whole land area affected", 
       y = "Number of leases")
```

```{r}
exposed_prawn_leases<-qld_leases_erosion%>%
   filter(grepl('Prawn', Species))
exposed_barramundi_leases<-qld_leases_erosion%>%
  filter(grepl('Barra', Species))
exposed_Redclaw_leases<-qld_leases_erosion%>%
  filter(grepl('Red', Species))
exposed_Freshwater_fish_leases<-qld_leases_erosion%>%
   filter(grepl('Freshwater fish', Species))
exposed_Hatchery_leases<-qld_leases_erosion%>%
  filter(grepl('Hatchery', Species))
exposed_Ornamental_leases<-qld_leases_erosion%>%
  filter(grepl('Orna', Species))
```

```{r}
st_write(exposed_prawn_leases, here("output_data/RESULTS/exposure_by_lease/exposed_prawn_leases.gpkg"), delete_layer = TRUE)
st_write(exposed_barramundi_leases, here("output_data/RESULTS/exposure_by_lease/exposed_barramundi_leases.gpkg"), delete_layer = TRUE)
st_write(exposed_Redclaw_leases, here("output_data/RESULTS/exposure_by_lease/exposed_Redclaw_leases.gpkg"), delete_layer = TRUE)
st_write(exposed_Freshwater_fish_leases, here("output_data/RESULTS/exposure_by_lease/exposed_Freshwater_fish_leases.gpkg"), delete_layer = TRUE)
st_write(exposed_Hatchery_leases, here("output_data/RESULTS/exposure_by_lease/exposed_Hatchery_leases.gpkg"), delete_layer = TRUE)
st_write(exposed_Ornamental_leases, here("output_data/RESULTS/exposure_by_lease/exposed_Ornamental_leases.gpkg"), delete_layer = TRUE)
```
```{r}
files_whole<-list.files(here("output_data/RESULTS/exposure_by_lease"), full.names = T)

all_whole<-lapply(files_whole, read_sf)

all_df_whole<-do.call(rbind, all_whole)
  
all_df2_whole<-all_df_whole %>% 
  as.data.frame(.) %>% 
  select(qldglb_, Species, Authority, affected_area_m2, lease_area_m2, propaffectedArea) %>%
rename(affected_area_proportion= propaffectedArea )

```
#check these before running always
```{r}
all_df2_whole[92,2]<- "Redclaw"
all_df2_whole[28,2]<- "Hatchery"
all_df2_whole[29,2]<- "Hatchery"
all_df2_whole[30,2]<- "Hatchery"
all_df2_whole[31,2]<- "Hatchery"
all_df2_whole[32,2]<- "Hatchery"
all_df2_whole[33,2]<- "Hatchery"
all_df2_whole[63,2]<- "Prawn/Redclaw"
all_df2_whole[91,2]<- "Prawn/Redclaw"


```

```{r}
ggplot(all_df2_whole) +
  aes(affected_area_proportion, fill= Species) +
  geom_histogram() +
  theme_classic() +
  scale_fill_viridis_d() +
  labs(x = "Prop. of Land in Leases affected", 
       y = "Number of Leases")
```
```{r}
ggplot(all_df2_whole) +
  aes(affected_area_proportion, fill = Species) +
  geom_histogram() +
  theme_classic() +
  scale_fill_viridis_d(option = "plasma") +
  labs(x = "Prop. of each lease affected", 
       y = "Number of leases") +
  theme(
    axis.title.x = element_text(size = 16),  # Increase X axis title size
    axis.title.y = element_text(size = 16),  # Increase Y axis title size
    axis.text.x = element_text(size = 14),   # Increase X axis text size
    axis.text.y = element_text(size = 14)    # Increase Y axis text size
)
```


```{r}
qld_leases_erosion_percent<-qld_leases_erosion%>%
  mutate(percentage= propaffectedArea*100)
```
```{r}
qld_leases_erosion_productiveGT_percent<-qld_leases_erosion_productiveGT%>%
  mutate(percentage= propaffectedArea*100)
```
```{r}
qld_leases_erosion_productiveGEE_percent<-qld_leases_erosion_productiveGEE%>%
  mutate(percentage= propaffectedArea*100)
```



```{r}
Exposed_leases_with_ponds_percent<-Exposed_leases_with_ponds_GEE%>%
  mutate(percentage= propaffectedArea*100)
```


```{r}
tmap_mode("plot")+
  tm_shape(QLD_map) +
  tm_polygons(col= "gray", alpha=0.2)+
  tm_shape(shp = qld_leases_erosion_percent) +
 tm_bubbles(size = 0.3, 
            col = "percentage",
           title.col = "% of the area exposed by 2100",
           palette = viridis(10),
           style= "quantile")+
tm_layout(legend.position = c("right", "top"),
           inner.margins = c(0.1, 0.1, 0.1, 0.3))

```
```{r}
tmap_mode("plot") +
  tm_shape(QLD_map) +
  tm_polygons(col = "gray", alpha = 0.2) +
  tm_shape(shp = qld_leases_erosion_percent) +
  tm_bubbles(size = 0.3, 
             col = "percentage",
             title.col = "% of the area exposed by 2100",
             palette = viridis(10),
             style = "quantile") +
  tm_layout(legend.position = c("right", "top"),
            inner.margins = c(0.1, 0.1, 0.1, 0.3),
            title.size = 1.5)  # Adjust the size value as needed
```
```{r}


# Assuming QLD_map and qld_leases_erosion_percent are sf objects
# Plot base map
ggplot() +
  geom_sf(data = QLD_map, fill = "gray", alpha = 0.2) +  # Base map with QLD_map
  geom_point(data = qld_leases_erosion_percent, aes(geometry = geometry, color = -percentage), 
             alpha = 0.8, stat = "sf_coordinates") +  # Bubbles with size and color mapped
  scale_size_continuous(range = c(1, 10)) +  # Adjust the size range of the bubbles
  scale_color_viridis_c(name = "% of the area exposed by 2100", option = "viridis") +  # Color scale with viridis palette and title
  theme_minimal() +  # Minimal theme for better visualization
  theme(
    legend.position =  "right",  # Adjust legend position
    legend.title = element_text(size = 12),  # Adjust legend title size
    plot.margin = margin(10, 30, 10, 10)  # Adjust plot margins
    )


```

```{r}

# Assuming QLD_map and qld_leases_erosion_percent are sf objects
# Plot base map
ggplot() +
  geom_sf(data = QLD_map, fill = "gray", alpha = 0.2) +  # Base map with QLD_map
  geom_point(data = qld_leases_erosion_percent, aes(geometry = geometry, color = -percentage), 
             alpha = 0.8, stat = "sf_coordinates") +  # Bubbles with size and color mapped
  scale_size_continuous(range = c(1, 10)) +  # Adjust the size range of the bubbles
  scale_color_viridis_c(name = "% of the area exposed by 2100", option = "plasma") +  # Color scale with viridis palette and title
  theme_minimal() +  # Minimal theme for better visualization
  theme(
    legend.position =  "right",  # Adjust legend position
    legend.title = element_text(size = 12),  # Adjust legend title size
    plot.margin = margin(10, 30, 10, 10)  # Adjust plot margins
    )


```


```{r}
Leases_exposure_hotspots<-ggplot() +
  geom_sf(data = QLD_map, fill = "gray", alpha = 0.2) +  # Base map with QLD_map
  geom_point(data = qld_leases_erosion_percent, aes(geometry = geometry, color = percentage), 
             alpha = 0.8, stat = "sf_coordinates") +  # Bubbles with color mapped
  scale_size_continuous(range = c(1, 10)) +  # Adjust the size range of the bubbles
  scale_color_viridis_c(name = "Percentage of the leases exposed by 2100", option = "plasma") +  # Color scale with viridis palette and title
  theme_minimal() +  # Minimal theme for better visualization
  theme(
    legend.position =  "bottom",  # Adjust legend position
    legend.title = element_text(size = 12),  # Adjust legend title size
    plot.margin = margin(10, 30, 10, 10)  # Adjust plot margins
  ) +
  labs(x = "Longitude", y = "Latitude")  # Add labels to the x and y axes

```
#plot leases exposure hotspots
```{r}
plot(Leases_exposure_hotspots)
```

```{r}
ggplot() +
  geom_sf(data = QLD_map, fill = "gray", alpha = 0.2) +  # Base map with QLD_map
  geom_point(data = qld_leases_erosion_productiveGT_percent, aes(geometry = geometry, color = -percentage), 
             alpha = 0.8, stat = "sf_coordinates") +  # Bubbles with color mapped
  scale_size_continuous(range = c(1, 10)) +  # Adjust the size range of the bubbles
  scale_color_viridis_c(name = "percentage of area exposed by 2100", option = "plasma") +  # Color scale with viridis palette and title
  theme_minimal() +  # Minimal theme for better visualization
  theme(
    legend.position =  "right",  # Adjust legend position
    legend.title = element_text(size = 12),  # Adjust legend title size
    plot.margin = margin(10, 30, 10, 10)  # Adjust plot margins
  ) +
  labs(x = "Longitude", y = "Latitude")  # Add labels to the x and y axes

```
```{r}
ggplot() +
  geom_sf(data = QLD_map, fill = "gray", alpha = 0.2) +  # Base map with QLD_map
  geom_point(data = qld_leases_erosion_productiveGEE_percent, aes(geometry = geometry, color = -percentage), 
             alpha = 0.8, stat = "sf_coordinates") +  # Bubbles with color mapped
  scale_size_continuous(range = c(1, 10)) +  # Adjust the size range of the bubbles
  scale_color_viridis_c(name = "% of the area exposed by 2100", option = "viridis") +  # Color scale with viridis palette and title
  theme_minimal() +  # Minimal theme for better visualization
  theme(
    legend.position =  "right",  # Adjust legend position
    legend.title = element_text(size = 12),  # Adjust legend title size
    plot.margin = margin(10, 30, 10, 10)  # Adjust plot margins
  ) +
  labs(x = "Longitude", y = "Latitude")  # Add labels to the x and y axes

```
```{r}
tmap_mode("plot")+
  tm_shape(QLD_map) +
  tm_polygons(col= "gray", alpha=0.2)+
  tm_shape(shp = qld_leases_erosion_productiveGEE_percent) +
 tm_bubbles(size = 0.3, 
            col = "percentage",
           title.col = "% of the area exposed by 2100",
           palette = viridis(10),
           style= "quantile")+
tm_layout(legend.position = c("right", "top"),
           inner.margins = c(0.1, 0.1, 0.1, 0.3))

```

```{r}
tmap_mode("plot")+
  tm_shape(QLD_map) +
  tm_polygons(col= "gray", alpha=0.2)+
  tm_shape(shp = qld_leases_erosion_productiveGT_percent) +
 tm_bubbles(size = 0.3, 
            col = "percentage",
           title.col = "% of the area exposed by 2100",
           palette = viridis(10),
           style= "quantile")+
tm_layout(legend.position = c("right", "top"),
           inner.margins = c(0.1, 0.1, 0.1, 0.3))

```
#plots with productive leases that show ponds in GEE
```{r}
# Ensure percentage is numeric and represents a value from 0 to 100
Exposed_leases_with_ponds_percent$percentage <- as.numeric(Exposed_leases_with_ponds_percent$percentage)

# If the values are too large, you may need to divide by a factor to scale them correctly
# For example, if they are counts and you want them as percentages, you might do:
# Exposed_leases_with_ponds_percent$percentage <- Exposed_leases_with_ponds_percent$percentage / 1e6

# Check the range of the values
summary(Exposed_leases_with_ponds_percent$percentage)

```
```{r}
# Normalize percentage values to be between 0 and 100
total_value <- max(Exposed_leases_with_ponds_percent$percentage, na.rm = TRUE)

# Create new percentage column
Exposed_leases_with_ponds_percent$normalized_percentage <- (Exposed_leases_with_ponds_percent$percentage / total_value) * 100

# Check the new range
summary(Exposed_leases_with_ponds_percent$normalized_percentage)
```

#final map of leases exposed that contain ponds
```{r}
productive_Leases_exposure_hotspots <- ggplot() +
  geom_sf(data = QLD_map, fill = "gray", alpha = 0.2) +  # Base map with QLD_map
  geom_point(data = Exposed_leases_with_ponds_percent, aes(geometry = geometry, color = normalized_percentage), 
             alpha = 0.8, stat = "sf_coordinates", size = 3) +  # Adjust size if needed
  scale_color_viridis_c(
    name = "Percentage of Leases\n Exposed by 2100",
    option = "plasma",
    limits = c(0, 100),
    breaks = seq(0, 100, 20),  # Adjust breaks to your preference
    labels = scales::percent_format(scale = 1)  # Format as percentage
  ) +
  theme_minimal() +  # Minimal theme for better visualization
  theme(
    legend.position = "right",
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 8),
    plot.margin = margin(10, 30, 10, 10)
  ) +
  labs(x = "Longitude", y = "Latitude")

# Print the plot
print(productive_Leases_exposure_hotspots)
```


#test all leases with ponds exposure even without known species
```{r}
ggplot(Exposed_leases_with_ponds_percent) +
  aes(normalized_percentage, fill = Species) +
  geom_histogram() +
  theme_classic() +
  scale_fill_viridis_d(option = "plasma", na.value = "grey50") +
  labs(x = "Prop. of each lease affected", 
       y = "Number of leases") +
  theme(
    axis.title.x = element_text(size = 16),  # Increase X axis title size
    axis.title.y = element_text(size = 16),  # Increase Y axis title size
    axis.text.x = element_text(size = 14),   # Increase X axis text size
    axis.text.y = element_text(size = 14)    # Increase Y axis text size
)
```

#the productive areas by 1/3
```{r}
ggplot(Exposed_leases_with_ponds_percent) +
  aes(cut(normalized_percentage, breaks = c(0, 33.3, 66.6, 100)), fill = Species) +
  geom_bar() +
  theme_classic() +
  scale_fill_viridis_d(option = "plasma", na.value = "grey50") +
  labs(x = "Prop. of each lease affected", 
       y = "Number of leases") +
  theme(
    axis.title.x = element_text(size = 16),  # Increase X axis title size
    axis.title.y = element_text(size = 16),  # Increase Y axis text size
    axis.text.x = element_text(size = 14),   # Increase X axis text size
    axis.text.y = element_text(size = 14)    # Increase Y axis text size
)
```



#the productive areas by half
```{r}
ggplot(Exposed_leases_with_ponds_percent) +
  aes(cut(normalized_percentage, breaks = c(0, 50, 100)), fill = Species) +
  geom_bar() +
  theme_classic() +
  scale_fill_viridis_d(option = "plasma", na.value = "grey50") +
  labs(x = "Prop. of each lease affected", 
       y = "Number of leases") +
  theme(
    axis.title.x = element_text(size = 16),  # Increase X axis title size
    axis.title.y = element_text(size = 16),  # Increase Y axis text size
    axis.text.x = element_text(size = 14),   # Increase X axis text size
    axis.text.y = element_text(size = 14)    # Increase Y axis text size
)
```
#details by species considering the full land dedicated to aquaculture or at leases leased for aquaculture

#amount of farms/leases exposed by species and the amount of area in each lease and amount of area exposed 

#data on prawn leases and farms
```{r}
unique(prawn_leases$qldglb_)#55
unique(prawn_leases$Authority)#39
unique(exposed_prawn_leases$qldglb_)#54
unique(exposed_prawn_leases$Authority)#38
```

```{r}
sum(prawn_leases$lease_area_km2)#39.02
sum(exposed_prawn_leases$lease_area_km2)#38.60
sum(exposed_prawn_leases$lease_area_km2)/sum(prawn_leases$lease_area_km2)*100

```

#barramundi leases and farms
```{r}
#leases
unique(barramundi_leases$qldglb_)#50
unique(exposed_barramundi_leases$qldglb_)#22
#farms
unique(barramundi_leases$Authority)#34
unique(exposed_barramundi_leases$Authority)#16
```

```{r}
sum(barramundi_leases$lease_area_km2)#143.18
sum(exposed_barramundi_leases$lease_area_km2)#11.12
sum(exposed_barramundi_leases$lease_area_km2)/sum(barramundi_leases$lease_area_km2)*100 #7.7%
```
#red claw leases and farms
```{r}
#leases
unique(Redclaw_leases$qldglb_)#75
unique(exposed_Redclaw_leases$qldglb_)#6
#farms
unique(Redclaw_leases$Authority)#66
unique(exposed_Redclaw_leases$Authority)#6
```

```{r}
sum(Redclaw_leases$lease_area_km2)#105.2
sum(exposed_Redclaw_leases$lease_area_km2)#2.07
sum(exposed_Redclaw_leases$lease_area_km2)/sum(Redclaw_leases$lease_area_km2)*100 #1.96%
```
#Freshwater fish leases and farms
```{r}
#leases
unique(Freshwater_fish_leases$qldglb_)#39
unique(exposed_Freshwater_fish_leases$qldglb_)#5
#farms
unique(Freshwater_fish_leases$Authority)#34
unique(exposed_Freshwater_fish_leases$Authority)#4
```

```{r}
sum(Freshwater_fish_leases$lease_area_km2)#23.1
sum(exposed_Freshwater_fish_leases$lease_area_km2)#1.59
sum(exposed_Freshwater_fish_leases$lease_area_km2)/sum(Freshwater_fish_leases$lease_area_km2)*100 #  6.89%
```
#Hatchery leases and farms
```{r}
#leases
unique(Hatchery_leases$qldglb_)#10
unique(exposed_Hatchery_leases$qldglb_)#6
#farms
unique(Hatchery_leases$Authority)#8
unique(exposed_Hatchery_leases$Authority)#4
```

```{r}
sum(Hatchery_leases$lease_area_km2)#1.84
sum(exposed_Hatchery_leases$lease_area_km2)#0.69
sum(exposed_Hatchery_leases$lease_area_km2)/sum(Hatchery_leases$lease_area_km2)*100 # 37.80%
```
#Ornamentals leases and farms
```{r}
#leases
unique(Ornamental_leases$qldglb_)#13
unique(exposed_Ornamental_leases$qldglb_)#1
#farms
unique(Ornamental_leases$Authority)#12
unique(exposed_Ornamental_leases$Authority)#1
```

```{r}
sum(Ornamental_leases$lease_area_km2)#
sum(exposed_Ornamental_leases$lease_area_km2)#
sum(exposed_Ornamental_leases$lease_area_km2)/sum(Ornamental_leases$lease_area_km2)*100 # %
```
#difference between leases with known species and leases that we don't know the species are due to not having available data on all species that have leases - most of the time due to not being a productive lease
```{r}
sum(Ornamental_leases$lease_area_km2)+sum(Hatchery_leases$lease_area_km2)+sum(Freshwater_fish_leases$lease_area_km2)+sum(Redclaw_leases$lease_area_km2)+sum(barramundi_leases$lease_area_km2)+sum(prawn_leases$lease_area_km2)#318.30
```
```{r}
sum(qld_leases$lease_area_km2)
```


