---
title : "Ponds_in_leases_erosion_and_histograms_Revision_V3_mar_2025"
output: html_document
date: "2025-February_March"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#load packages I will need for that analysis
```{r}
library(tidyverse)
library(here)
library(tmap)
library(sf)
library(ggplot2)
library(dplyr)
library(cowplot)
library(ggrepel)
```

```{r}
Final_species2024_new<-st_read(here("output_data/RESULTS/Final_species2024_new.gpkg"))
```
#filter out the leases we have found that are not productive to make a final leases layer
```{r}
values_to_exclude<- c("2020BC0019", "2007BC0184")
```

# Get the row indices to exclude using the grep() function
```{r}
rows_to_exclude <- grep(paste(values_to_exclude, collapse = "|"), Final_species2024_new$Authority)
```
# Filter the data frame
```{r}
Final_species2024_leases <- Final_species2024_new[-rows_to_exclude, ]
```

#DAF informed that some hatcheries were in reality marine finfish aquaculture so lets change it - November 2024 lots: 	
#53SP331336 and 276WD130 are finfish and 20sp134109 and 1RP6959 are hatchery and marine finfish
```{r}
Final_species2024_leases[128,2]<- "Marine finfish"
Final_species2024_leases[263,2]<- "Marine finfish"
Final_species2024_leases[75,2]<- "Hatchery"
Final_species2024_leases[99,2]<- "Hatchery"
Final_species2024_leases[99,3]<- "2005BC0299"

```

```{r}
st_write(Final_species2024_leases,here("output_data/RESULTS/Final_species2024_leases.gpkg"), delete_layer = TRUE)
 
```

#these are the productive ponds that use ponds system or any water body in open areas that could be detected by GEE and Ground truthed by our team

# load data
#Ponds obtained afte Google Earth Engine (GEE) 
#in this code we are using NDWI percentile 20th (to find water bodies that could be dry sometimes)+ 80th Percentile (areas with constant water filling) +NDWI sum (water bodies generally filled with water)

```{r}
QLD_aqua_ponds_combined_shapefile_NDWI_p20<-st_read(here("output_data/QLD_aqua_ponds_combined_shapefile_NDWI_p20.shp"))
```
```{r}
QLD_aqua_ponds_combined_shapefile_NDWI_p80<-st_read(here("output_data/QLD_aqua_ponds_combined_shapefile_NDWI_p80.shp"))
```
```{r}
QLD_aqua_ponds_combined_shapefile_NDWI_sum_raw<- st_read(here("raw_data/GEE_exports_20_21/GEE_vectors_QLDCOAST_20_21/ndwi_sum_thresh_vector_QLDCOAST_20_21/ndwi_sum_thresh_vector_QLDCOAST_aqua_20_21.shp"))
```
```{r}
QLD_aqua_ponds_combined_shapefile_NDWI_sum<-st_transform(QLD_aqua_ponds_combined_shapefile_NDWI_sum_raw, 3577)
```

#bind all the pond results together_ all of them were outputs of Google Earth Engine (GEE) with the index NDWI

```{r}
QLD_ponds_GEEOutput<- bind_rows(QLD_aqua_ponds_combined_shapefile_NDWI_sum, QLD_aqua_ponds_combined_shapefile_NDWI_p80, QLD_aqua_ponds_combined_shapefile_NDWI_p20)
```

#reprojected the data to Australian Albers CRS 3577

```{r}
QLD_ponds_GEE_reproj<-st_transform(QLD_ponds_GEEOutput, 3577)
```

#dissolve the ponds layer 
```{r}
QLD_GEE_ponds_diss<-QLD_ponds_GEE_reproj%>%
  mutate(diss = 1) %>% #create column to dissolve by
  # group_by(diss) %>% #group by column you created
  summarise(diss2 = sum(diss, na.rm = T)) #combine column into one new variable and ignore NA values
  
```

```{r}
QLD_ponds_in_leases<-st_intersection(QLD_GEE_ponds_diss, Final_species2024_leases)
```

#calculate the area of the ponds in each farm
```{r}
QLD_ponds_in_leases<-QLD_ponds_in_leases%>%
  mutate(pond_area_m2 = as.numeric(st_area(.)))%>%
 mutate(pond_area_km2 = pond_area_m2/1e6)%>%
  mutate(pond_area_hectares = pond_area_m2/1e4)
```

```{r}
st_write(QLD_ponds_in_leases, here("output_data/RESULTS/QLD_ponds_in_leases.gpkg"), delete_layer = TRUE) 
```


#size of ponds all together in m2, km2 and hectares 
```{r}
area_of_ponds_in_leases_m2<-sum(QLD_ponds_in_leases$pond_area_m2)
area_of_ponds_in_leases_km2<-sum(QLD_ponds_in_leases$pond_area_km2)
area_of_ponds_in_leases_hectares<-sum(QLD_ponds_in_leases$pond_area_hectares)
```

#DISSOLVED - you can also load data already dissolved that you have done in the code earlier, we had already transformed it to Australian Alvers CRS 3577 as well. 

```{r}
QLD_coastal_erosion_allcomp_diss<-st_read(here("output_data/QLD_coastal_erosion_allcomp_diss.shp"))
```

# clean the columns before intersecting selecting only the ones we will need (which is the geometry)
```{r}
QLD_coastal_erosion<-QLD_coastal_erosion_allcomp_diss%>%
  select(geometry)
```


#separate by species group in each farm before intersecting for better control

```{r}
prawn_ponds_in_leases<-QLD_ponds_in_leases%>%
 filter(grepl('Prawn', Species))%>%
mutate(pond_area_m2 = as.numeric(st_area(.)))%>%
mutate(pond_area_km2 = pond_area_m2/1e6)%>%
mutate(pond_area_hectares = pond_area_m2/1e4)
```
#Calculate prawn productivity
# PRAWN (1056 tonnes/km2 is the mean)production and the 20% mortality rate gives us an 845 tonnes per km2 yield and other minimum(600tonnes) and maximum(1120tonnes) scenarios
```{r}
calculate_productivity <- function(density_min = 25,    # specimens per m2
                                 density_max = 40,
                                 weight_min = 30,       # grams
                                 weight_max = 35,
                                 loss_rate = 0.20,      # 20% loss
                                 total_area = 11.7144) { # km2
  
  # Calculate means
  density_mean <- mean(c(density_min, density_max))
  weight_mean <- mean(c(weight_min, weight_max))
  
  # Calculate all combinations
  productivity <- data.frame(
    scenario = c("Minimum", "Mean", "Maximum"),
    density = c(density_min, density_mean, density_max),
    weight = c(weight_min, weight_mean, weight_max),
    total_area_km2 = total_area
  )
  
  # Calculate productivity
  productivity$kg_per_m2 <- (productivity$density * productivity$weight) / 1000  # convert g to kg
  productivity$kg_per_m2_with_loss <- productivity$kg_per_m2 * (1 - loss_rate)
  productivity$tonnes_per_km2 <- productivity$kg_per_m2_with_loss * 1000000  # convert to tonnes per km2
  productivity$total_production_tonnes <- productivity$tonnes_per_km2 * productivity$total_area_km2
  
  return(productivity)
}

# Use the function
prawn_productivity <- calculate_productivity()
print(prawn_productivity)
```

```{r}
prawn_ponds_in_leases<-prawn_ponds_in_leases%>%
mutate(
    expected_production_min = pond_area_km2 * prawn_productivity$tonnes_per_km2[1],  # minimum scenario
    expected_production_mean = pond_area_km2 * prawn_productivity$tonnes_per_km2[2],  # mean scenario
    expected_production_max = pond_area_km2 * prawn_productivity$tonnes_per_km2[3]   # maximum scenario
  )
```

```{r}
sum(prawn_ponds_in_leases$pond_area_m2)
sum(prawn_ponds_in_leases$pond_area_hectares)
sum(prawn_ponds_in_leases$pond_area_km2)
sum(prawn_ponds_in_leases$expected_production_min)
sum(prawn_ponds_in_leases$expected_production_mean)
sum(prawn_ponds_in_leases$expected_production_max)
```


#if I want to know how much pond area exists in QLD for each species then I can do this

#Barramundi by farm

```{r}
Barramundi_ponds_in_leases<- QLD_ponds_in_leases%>%
  filter(grepl('Barramundi', Species))%>%
   mutate(pond_area_m2 = as.numeric(st_area(.)))%>%
mutate(pond_area_km2 = pond_area_m2/1e6)%>%
mutate(pond_area_hectares = pond_area_m2/1e4)

```
#calculating barramundi productivity
```{r}
calculate_barramundi_productivity <- function(yield_min = 15,    # tonnes/hectare
                                            yield_max = 30,      # tonnes/hectare
                                            total_area = 2.15) { # km2
  
  # Calculate mean
  yield_mean <- mean(c(yield_min, yield_max))
  
  # Create data frame
  productivity <- data.frame(
    scenario = c("Minimum", "Mean", "Maximum"),
    tonnes_per_hectare = c(yield_min, yield_mean, yield_max),
    total_area_km2 = total_area
  )
  
  # Calculate tonnes per km2 
  # Convert tonnes/hectare to tonnes/km2: 
  # 1 km2 = 100 hectares
  productivity$tonnes_per_km2 <- productivity$tonnes_per_hectare * 100
  
  # Calculate total production
  productivity$total_production_tonnes <- productivity$tonnes_per_km2 * productivity$total_area_km2
  
  return(productivity)
}

# Use the function
barramundi_productivity <- calculate_barramundi_productivity()
print(barramundi_productivity)
```

#barramundi productivity min, mean, max
#Using the mean values # 2250 tonnes per km2)
```{r}
Barramundi_ponds_in_leases <- Barramundi_ponds_in_leases %>%
  mutate(
    expected_production_min = pond_area_km2 * barramundi_productivity$tonnes_per_km2[1],  # minimum scenario
    expected_production_mean = pond_area_km2 * barramundi_productivity$tonnes_per_km2[2],  # mean scenario
    expected_production_max = pond_area_km2 * barramundi_productivity$tonnes_per_km2[3]   # maximum scenario
  )
```


#if there was no impact of SLR then this is the expected Barramundi production
```{r}
sum(Barramundi_ponds_in_leases$pond_area_m2)
sum(Barramundi_ponds_in_leases$pond_area_hectares) 
sum(Barramundi_ponds_in_leases$pond_area_km2)
sum(Barramundi_ponds_in_leases$expected_production_min)
sum(Barramundi_ponds_in_leases$expected_production_mean)
sum(Barramundi_ponds_in_leases$expected_production_max)
```
# Save the results of productivity
```{r}

write.csv(prawn_productivity, 
          here("output_data/RESULTS/prawn_productivity_scenarios.csv"), 
          row.names = FALSE)

write.csv(barramundi_productivity, 
          here("output_data/RESULTS/barramundi_productivity_scenarios.csv"), 
          row.names = FALSE)
```
#save as excel files
```{r}
library(writexl)

# Save as Excel files
write_xlsx(prawn_productivity, 
           here("output_data/RESULTS/prawn_productivity_scenarios.xlsx"))

write_xlsx(barramundi_productivity, 
           here("output_data/RESULTS/barramundi_productivity_scenarios.xlsx"))
```
# Summary statistics including all scenarios
```{r}
# Summary statistics including all scenarios
prawn_summary <- data.frame(
  Species = "Prawn",
  Total_area_m2 = sum(prawn_ponds_in_leases$pond_area_m2),
  Total_area_hectares = sum(prawn_ponds_in_leases$pond_area_hectares),
  Total_area_km2 = sum(prawn_ponds_in_leases$pond_area_km2),
  Total_production_min = sum(prawn_ponds_in_leases$expected_production_min),
  Total_production_mean = sum(prawn_ponds_in_leases$expected_production_mean),
  Total_production_max = sum(prawn_ponds_in_leases$expected_production_max)
)

barramundi_summary <- data.frame(
  Species = "Barramundi",
  Total_area_m2 = sum(Barramundi_ponds_in_leases$pond_area_m2),
  Total_area_hectares = sum(Barramundi_ponds_in_leases$pond_area_hectares),
  Total_area_km2 = sum(Barramundi_ponds_in_leases$pond_area_km2),
  Total_production_min = sum(Barramundi_ponds_in_leases$expected_production_min),
  Total_production_mean = sum(Barramundi_ponds_in_leases$expected_production_mean),
  Total_production_max = sum(Barramundi_ponds_in_leases$expected_production_max)
)

# Combine summaries
production_summary <- rbind(prawn_summary, barramundi_summary)

# Save results
write.csv(production_summary, 
          here("output_data/RESULTS/total_production_scenarios_summary.csv"), 
          row.names = FALSE)
```


#REDCLAW 
#Redclaw by farm
```{r}
Redclaw_ponds_in_leases<- QLD_ponds_in_leases%>%
  filter(grepl('Red', Species))%>%
 mutate(pond_area_m2 = as.numeric(st_area(.)))%>%
mutate(pond_area_km2 = pond_area_m2/1e6)%>%
  mutate(pond_area_hectares = pond_area_m2/1e4)
```
#if there was no impact of SLR then this is the expected Redclaw area
```{r}
sum(Redclaw_ponds_in_leases$pond_area_m2)
sum(Redclaw_ponds_in_leases$pond_area_hectares)
sum(Redclaw_ponds_in_leases$pond_area_km2)

```
#freshwater fish in farms
```{r}
Freshwater_fish_ponds_in_leases<- QLD_ponds_in_leases%>%
  filter(grepl('Freshwater fish', Species))%>%
 mutate(pond_area_m2 = as.numeric(st_area(.)))%>%
  mutate(pond_area_km2 = pond_area_m2/1e6) %>%
  mutate(pond_area_hectares = pond_area_m2/1e4)

```
#if there was no impact of SLR then this is the expected Freshwater fish ponds area
```{r}
sum(Freshwater_fish_ponds_in_leases$pond_area_m2)
sum(Freshwater_fish_ponds_in_leases$pond_area_hectares)
sum(Freshwater_fish_ponds_in_leases$pond_area_km2)

```

#HATCHERIES

#hatcheries by farm
```{r}
Hatchery_ponds_in_leases<- QLD_ponds_in_leases%>%
  filter(grepl('Hatchery', Species))%>%
  mutate(pond_area_m2 = as.numeric(st_area(.)))%>%
mutate(pond_area_km2 = pond_area_m2/1e6)%>%
  mutate(pond_area_hectares = pond_area_m2/1e4)
```

#if there was no impact of SLR then this is the expected hatchery ponds area
```{r}
sum(Hatchery_ponds_in_leases$pond_area_m2)
sum(Hatchery_ponds_in_leases$pond_area_hectares)
sum(Hatchery_ponds_in_leases$pond_area_km2)
```

#ORNAMENTAL
#by farm
```{r}
Ornamental_ponds_in_leases<- QLD_ponds_in_leases%>%
  filter(grepl('Orna', Species))%>%
  mutate(pond_area_m2 = as.numeric(st_area(.)))%>%
mutate(pond_area_km2 = pond_area_m2/1e6)%>%
  mutate(pond_area_hectares = pond_area_m2/1e4)

```

#if there was no impact of SLR then this is the expected ornamental ponds area
```{r}
sum(Ornamental_ponds_in_leases$pond_area_m2)
sum(Ornamental_ponds_in_leases$pond_area_hectares)
sum(Ornamental_ponds_in_leases$pond_area_km2)
```

```{r}
Unknown_species_ponds_in_leases<- QLD_ponds_in_leases%>%
  filter(grepl('other', Species))%>%
 mutate(pond_area_m2 = as.numeric(st_area(.)))%>%
mutate(pond_area_km2 = pond_area_m2/1e6)%>%
  mutate(pond_area_hectares = pond_area_m2/1e4)
```

#if there was no impact of SLR then this is the expected ornamental ponds area
```{r}
sum(Unknown_species_ponds_in_leases$pond_area_m2)
sum(Unknown_species_ponds_in_leases$pond_area_hectares)
sum(Unknown_species_ponds_in_leases$pond_area_km2)
```
#freshwater fish in farms
```{r}
Marine_fish_ponds_in_leases<- QLD_ponds_in_leases%>%
  filter(grepl('finfish', Species))%>%
 mutate(pond_area_m2 = as.numeric(st_area(.)))%>%
  mutate(pond_area_km2 = pond_area_m2/1e6) %>%
  mutate(pond_area_hectares = pond_area_m2/1e4)

```
#if there was no impact of SLR then this is the expected Freshwater fish ponds area
```{r}
sum(Marine_fish_ponds_in_leases$pond_area_m2)
sum(Marine_fish_ponds_in_leases$pond_area_hectares)
sum(Marine_fish_ponds_in_leases$pond_area_km2)

```

#NOW RUN EXPOSURE OVER EACH GROUP SPECIES

#intersect each species group aquaculture ponds found in GEE separated by FARMS with dissolved coastal erosion layer
```{r}
QLD_SLR_erosion_prawn_ponds_leases<-st_intersection(QLD_coastal_erosion, prawn_ponds_in_leases)

QLD_SLR_erosion_Barramundi_ponds_leases<-st_intersection(QLD_coastal_erosion, Barramundi_ponds_in_leases)

QLD_SLR_erosion_Redclaw_ponds_leases<-st_intersection(QLD_coastal_erosion, Redclaw_ponds_in_leases)

QLD_SLR_erosion_Freshwater_fish_ponds_leases<-st_intersection(QLD_coastal_erosion, Freshwater_fish_ponds_in_leases)

QLD_SLR_erosion_Ornamental_ponds_leases<-st_intersection(QLD_coastal_erosion, Ornamental_ponds_in_leases)

QLD_SLR_erosion_Hatchery_ponds_leases<-st_intersection(QLD_coastal_erosion, Hatchery_ponds_in_leases)

QLD_SLR_erosion_Marinefish_ponds_leases<-st_intersection(QLD_coastal_erosion, Marine_fish_ponds_in_leases)


```

#Create a Column and get the proportion of the ponds in each FARM that might be affected following erosion and SLR in 2100 
#Check were to do this conversion- mutate(area_km2= affected_area_m2/1e6)
#how much would be lost at 7.5%
```{r}
QLD_SLR_erosion_prawn_ponds_leases_75<-QLD_SLR_erosion_prawn_ponds_leases%>%
 ungroup(.) %>%
   mutate(affected_area_m2 = as.numeric(st_area(.)))%>%
  mutate(affected_area_km2 = affected_area_m2/1e6)%>%
  mutate(affected_area_proportion= affected_area_km2/pond_area_km2)%>%
  mutate(worst=ifelse(affected_area_proportion>=0.075, pond_area_km2, affected_area_proportion))%>%
   select(qldglb_,pond_area_m2, pond_area_km2, Species, Authority, geometry, affected_area_m2,affected_area_km2, affected_area_proportion, worst)
```

#sum the areas to check the effect of erosion 7.5%
```{r}
sum(prawn_ponds_in_leases$pond_area_km2)
sum(QLD_SLR_erosion_prawn_ponds_leases_75$pond_area_km2)
sum(QLD_SLR_erosion_prawn_ponds_leases_75$affected_area_km2)
sum(QLD_SLR_erosion_prawn_ponds_leases_75$worst)

```


#15% code threshold Barramundi
```{r}
QLD_SLR_erosion_Barramundi_ponds_leases_15<-QLD_SLR_erosion_Barramundi_ponds_leases%>%
   ungroup(.) %>%
  mutate(affected_area_m2 = as.numeric(st_area(.)))%>%
  mutate(affected_area_km2 = affected_area_m2/1e6)%>%
  mutate(affected_area_proportion= affected_area_km2/pond_area_km2)%>%
  mutate(worst=ifelse(affected_area_proportion>=0.15, pond_area_km2, affected_area_proportion))%>%
  select(qldglb_,pond_area_m2, pond_area_km2, Species, Authority, geometry, affected_area_m2,affected_area_km2, affected_area_proportion, worst)
```

#sum the areas to check the effect of erosion
```{r}
sum(Barramundi_ponds_in_leases$pond_area_km2)
sum(QLD_SLR_erosion_Barramundi_ponds_leases_15$pond_area_km2)
sum(QLD_SLR_erosion_Barramundi_ponds_leases_15$affected_area_km2)
sum(QLD_SLR_erosion_Barramundi_ponds_leases_15$worst)

```

```{r}
QLD_SLR_erosion_Redclaw_ponds_leases<-QLD_SLR_erosion_Redclaw_ponds_leases%>%
 ungroup(.) %>%
  mutate(affected_area_m2 = as.numeric(st_area(.)))%>%
  mutate(affected_area_km2 = affected_area_m2/1e6)%>%
  mutate(affected_area_proportion= affected_area_km2/pond_area_km2)%>%
  mutate(worst=ifelse(affected_area_proportion>=0.1, pond_area_km2, affected_area_proportion))%>%
  select(qldglb_,pond_area_m2, pond_area_km2, Species, Authority, geometry, affected_area_m2,affected_area_km2, affected_area_proportion, worst)
```

#sum the areas to check the effect of erosion
```{r}
sum(Redclaw_ponds_in_leases$pond_area_km2)
sum(QLD_SLR_erosion_Redclaw_ponds_leases$pond_area_km2)
sum(QLD_SLR_erosion_Redclaw_ponds_leases$affected_area_km2)
sum(QLD_SLR_erosion_Redclaw_ponds_leases$worst)

```

```{r}
QLD_SLR_erosion_Freshwater_fish_ponds_leases<-QLD_SLR_erosion_Freshwater_fish_ponds_leases%>%
   ungroup(.) %>%
   mutate(affected_area_m2 = as.numeric(st_area(.)))%>%
  mutate(affected_area_km2 = affected_area_m2/1e6)%>%
  mutate(affected_area_proportion= affected_area_km2/pond_area_km2)%>%
  mutate(worst=ifelse(affected_area_proportion>=0.1, pond_area_km2, affected_area_proportion))%>%
  select(qldglb_,pond_area_m2, pond_area_km2, Species, Authority, geometry, affected_area_m2,affected_area_km2, affected_area_proportion, worst)
```

#sum the areas to check the effect of erosion
```{r}
sum(Freshwater_fish_ponds_in_leases$pond_area_km2)
sum(QLD_SLR_erosion_Freshwater_fish_ponds_leases$pond_area_km2)
sum(QLD_SLR_erosion_Freshwater_fish_ponds_leases$affected_area_km2)
sum(QLD_SLR_erosion_Freshwater_fish_ponds_leases$worst)
```

```{r}
QLD_SLR_erosion_Ornamental_ponds_leases<-QLD_SLR_erosion_Ornamental_ponds_leases%>%
   ungroup(.) %>%
   mutate(affected_area_m2 = as.numeric(st_area(.)))%>%
  mutate(affected_area_km2 = affected_area_m2/1e6)%>%
  mutate(affected_area_proportion= affected_area_km2/pond_area_km2)%>%
  mutate(worst=ifelse(affected_area_proportion>=0.1, pond_area_km2, affected_area_proportion))%>%
  select(qldglb_,pond_area_m2, pond_area_km2, Species, Authority, geometry, affected_area_m2,affected_area_km2, affected_area_proportion, worst)
```

#sum the areas to check the effect of erosion
```{r}
sum(Ornamental_ponds_in_leases$pond_area_km2)
sum(QLD_SLR_erosion_Ornamental_ponds_leases$pond_area_km2)
sum(QLD_SLR_erosion_Ornamental_ponds_leases$affected_area_km2)
sum(QLD_SLR_erosion_Ornamental_ponds_leases$worst)
```
#hatchery erosion results
```{r}
QLD_SLR_erosion_Hatchery_ponds_leases<-QLD_SLR_erosion_Hatchery_ponds_leases%>%
    ungroup(.) %>%
   mutate(affected_area_m2 = as.numeric(st_area(.)))%>%
  mutate(affected_area_km2 = affected_area_m2/1e6)%>%
  mutate(affected_area_proportion= affected_area_km2/pond_area_km2)%>%
  mutate(worst=ifelse(affected_area_proportion>=0.1, pond_area_km2, affected_area_proportion))%>%
  select(qldglb_,pond_area_m2, pond_area_km2, Species, Authority, geometry, affected_area_m2,affected_area_km2, affected_area_proportion, worst)
```

#sum the areas to check the effect of erosion hatcheries
```{r}
sum(Hatchery_ponds_in_leases$pond_area_km2)
sum(QLD_SLR_erosion_Hatchery_ponds_leases$pond_area_km2)
sum(QLD_SLR_erosion_Hatchery_ponds_leases$affected_area_km2)
sum(QLD_SLR_erosion_Hatchery_ponds_leases$worst)

```
#RErosion over marine fish aquaculture
```{r}
QLD_SLR_erosion_Marinefish_ponds_leases<-QLD_SLR_erosion_Marinefish_ponds_leases%>%
    ungroup(.) %>%
   mutate(affected_area_m2 = as.numeric(st_area(.)))%>%
  mutate(affected_area_km2 = affected_area_m2/1e6)%>%
  mutate(affected_area_proportion= affected_area_km2/pond_area_km2)%>%
  mutate(worst=ifelse(affected_area_proportion>=0.1, pond_area_km2, affected_area_proportion))%>%
  select(qldglb_,pond_area_m2, pond_area_km2, Species, Authority, geometry, affected_area_m2,affected_area_km2, affected_area_proportion, worst)
```

#sum the areas to check the effect of erosion marine fish
```{r}
sum(Marine_fish_ponds_in_leases$pond_area_km2)
sum(QLD_SLR_erosion_Marinefish_ponds_leases$pond_area_km2)
sum(QLD_SLR_erosion_Marinefish_ponds_leases$affected_area_km2)
sum(QLD_SLR_erosion_Marinefish_ponds_leases$worst)
```


##saving the aquaculture Ponds in Queensland that are used for the spefific groups of species

```{r}
st_write(prawn_ponds_in_leases, here("output_data/QLD_Aquaculture_distribution/RESULTS/QLD_pond_by_lease/prawn_ponds_in_leases.gpkg"), delete_layer = TRUE)
st_write(Barramundi_ponds_in_leases, here("output_data/QLD_Aquaculture_distribution/RESULTS/QLD_pond_by_lease/ Barramundi_ponds_in_leases.gpkg"), delete_layer = TRUE)
st_write(Redclaw_ponds_in_leases, here("output_data/QLD_Aquaculture_distribution/RESULTS/QLD_pond_by_lease/Redclaw_ponds_in_leases.gpkg"), delete_layer = TRUE)
st_write(Freshwater_fish_ponds_in_leases, here("output_data/QLD_Aquaculture_distribution/RESULTS/QLD_pond_by_lease/Freshwaterfish_ponds_in_leases.gpkg"), delete_layer = TRUE)
st_write(Hatchery_ponds_in_leases, here("output_data/QLD_Aquaculture_distribution/RESULTS/QLD_pond_by_lease/Hatchery_ponds_in_leases.gpkg"), delete_layer = TRUE)
st_write(Ornamental_ponds_in_leases, here("output_data/QLD_Aquaculture_distribution/RESULTS/QLD_pond_by_lease/Ornamental_ponds_in_leases.gpkg"), delete_layer = TRUE)
st_write(Marine_fish_ponds_in_leases, here("output_data/QLD_Aquaculture_distribution/RESULTS/QLD_pond_by_lease/Marine_fish_ponds_in_leases.gpkg"), delete_layer = TRUE)
```
#saving the exposure of SLR over the productive farm Ponds of each species group in Queensland that are within leases used for aquaculture 

```{r}
st_write(QLD_SLR_erosion_prawn_ponds_leases, here("output_data/QLD_Aquaculture_distribution/RESULTS/QLD_SLR_by_leases/QLD_SLR_erosion_Prawn_ponds_leases.gpkg"), delete_layer = TRUE)
st_write(QLD_SLR_erosion_Barramundi_ponds_leases, here("output_data/QLD_Aquaculture_distribution/RESULTS/QLD_SLR_by_leases/QLD_SLR_erosion_Barramundi_ponds_leases.gpkg"), delete_layer = TRUE)
st_write(QLD_SLR_erosion_Redclaw_ponds_leases, here("output_data/QLD_Aquaculture_distribution/RESULTS/QLD_SLR_by_leases/QLD_SLR_erosion_Redclaw__ponds_leases.gpkg"), delete_layer = TRUE)
st_write(QLD_SLR_erosion_Hatchery_ponds_leases, here("output_data/QLD_Aquaculture_distribution/RESULTS/QLD_SLR_by_leases/QLD_SLR_erosion_Hatchery_ponds_leases.gpkg"), delete_layer = TRUE)
st_write(QLD_SLR_erosion_Freshwater_fish_ponds_leases, here("output_data/QLD_Aquaculture_distribution/RESULTS/QLD_SLR_by_leases/QLD_SLR_erosion_Freshwater_fish__ponds_leases.gpkg"), delete_layer = TRUE)
st_write(QLD_SLR_erosion_Ornamental_ponds_leases, here("output_data/QLD_Aquaculture_distribution/RESULTS/QLD_SLR_by_leases/QLD_SLR_erosion_Ornamental_ponds_leases.gpkg"), delete_layer = TRUE)
st_write(QLD_SLR_erosion_Marinefish_ponds_leases, here("output_data/QLD_Aquaculture_distribution/RESULTS/QLD_SLR_by_leases/QLD_SLR_erosion_Marinefish_ponds_leases.gpkg"), delete_layer = TRUE)


```
#START FROM HERE TO MAKE GRAPHICS


#load_map
#Queensland state map already reprojected 
```{r}
Qld_map<-st_read(here("output_data/QLD_map.shp"))
```
#  histograms building for leases results

```{r}
# List files
files <- list.files(here("output_data/QLD_Aquaculture_distribution/RESULTS/QLD_SLR_by_leases"), 
                    full.names = TRUE)

# Modified reading function with different handling for different file types
read_and_process <- function(file) {
  df <- read_sf(file)
  filename <- basename(file)
  
  # For Barramundi and Prawn files (which have different structure)
  if(grepl("Barramundi|Prawn", filename)) {
    # These files need to have affected areas calculated
    if(!"affected_area_km2" %in% colnames(df)) {
      df <- df %>%
        mutate(
          affected_area_m2 = as.numeric(st_area(.)),
          affected_area_km2 = affected_area_m2/1e6,
          affected_area_proportion = affected_area_km2/pond_area_km2
        )
    }
  }
  
  # Select common columns (using any_of to handle different column names)
  df %>%
    select(Species, Authority, pond_area_km2, 
           affected_area_km2, affected_area_proportion, 
           any_of(c("geometry", "geom")))
}

# Try reading all files with the new function
all <- lapply(files, read_and_process)

# Combine all files
all_df <- do.call(rbind, all)

# Check the result
print(head(all_df))
print(table(all_df$Species))
```


#TAKE CARE HERE AND CHECK EVERYTHING AHEAD
```{r}
all_df[22,1]<- "Hatchery"
all_df[23,1]<- "Hatchery"
all_df[50,1]<- "Prawn/Redclaw"
all_df[75,1]<- "Prawn/Redclaw"


```

```{r}
ggplot(all_df) +
  aes(affected_area_proportion) +
  geom_histogram() +
  facet_wrap(facets = "Species") +
  theme_classic() +
    labs(x = "Prop. area affected", 
       y = "Number of farms")
```
```{r}
ggplot(all_df) +
  aes(affected_area_proportion, fill = Species) +
  geom_histogram() +
  theme_classic() +
  scale_fill_viridis_d() +
  labs(x = "Proportion of productive ponds affected ", 
       y = "Number of lots")
theme(
    axis.title.x = element_text(size = 16),  # Increase X axis title size
    axis.title.y = element_text(size = 16),  # Increase Y axis title size
    axis.text.x = element_text(size = 14),   # Increase X axis text size
    axis.text.y = element_text(size = 14)    # Increase Y axis text size
)
```
```{r}
#viridis plasma option
ggplot(all_df) +
  aes(affected_area_proportion, fill = Species) +
  geom_histogram() +
  theme_classic() +
  scale_fill_viridis_d(option="plasma") +
  labs(x = "Proportion of productive ponds affected ", 
       y = "Number of lots")
theme(
    axis.title.x = element_text(size = 16),  # Increase X axis title size
    axis.title.y = element_text(size = 16),  # Increase Y axis title size
    axis.text.x = element_text(size = 14),   # Increase X axis text size
    axis.text.y = element_text(size = 14)    # Increase Y axis text size
)
```
#viridis bar plot ponds exposure
```{r}
plot <- ggplot(all_df) +
  aes(affected_area_proportion, fill = Species) +
  geom_histogram() +
  theme_classic() +
  scale_fill_viridis_d() +
  labs(x = "Proportion of productive ponds affected", 
       y = "Number of Lots") +
  theme(legend.position = "none")  # Remove legend from the plot

# Extract the legend
legend2<- get_legend(
  ggplot(all_df) +
    aes(affected_area_proportion, fill = Species) +
    geom_histogram() +
    scale_fill_viridis_d() +
    theme_classic()
)
```
```{r}

# Arrange the plot and the legend
final_plot <- plot_grid(plot, legend2, ncol = 1, rel_widths = c(1, 0.3))

# Display the final plot
print(final_plot)
```

#plot pont exposure with plasma option
```{r}
plot_plasma <- ggplot(all_df) +
  aes(affected_area_proportion, fill = Species) +
  geom_histogram() +
  theme_classic() +
  scale_fill_viridis_d(option = "plasma") +
  labs(x = "Proportion of productive ponds affected", 
       y = "Number of Lots") +
  theme(legend.position = "none")  # Remove legend from the plot
```


```{r}
# Extract the legend
legend2_plasma<-get_legend(
  ggplot(all_df) +
    aes(affected_area_proportion, fill = Species) +
    geom_histogram() +
    scale_fill_viridis_d(option = "plasma")) +
    theme_classic()

```
#plasma plot
```{r}

# Arrange the plot and the legend
final_plot_plasma <- plot_grid(plot_plasma, legend2_plasma, ncol = 1, rel_widths = c(1, 0.3))

# Display the final plot
print(final_plot_plasma)
```

#number of sites  (all, lots/leases, farms, exposed)
```{r}
unique(QLD_ponds_in_leases$Authority)#192
unique(qld_leases_erosion$Authority)#90
unique (qld_leases_erosion_productive$Authority)#64
unique(Final_species2024_leases_productive$Authority)#190
unique(qld_leases$Authority)#276
unique (qld_leases_erosion_productive$qldglb_)#82
unique(Final_species2024_leases_productive$qldglb_)#225

```
#number of farms that have ponds 
```{r}
#number of farms with ponds
unique(prawn_ponds_in_leases$Authority) #36
unique(Barramundi_ponds_in_leases$Authority) #29
unique(Redclaw_ponds_in_leases$Authority) #52
unique(Freshwater_fish_ponds_in_leases$Authority)#22
unique(Hatchery_ponds_in_leases$Authority)#4
unique(Ornamental_ponds_in_leases$Authority)#4
unique(Marine_fish_ponds_in_leases$Authority)#1
```
```{r}
#number of farms with exposed ponds 
unique(QLD_SLR_erosion_prawn_ponds_leases$Authority) #32
unique(QLD_SLR_erosion_Barramundi_ponds_leases$Authority)#12
unique(QLD_SLR_erosion_Redclaw_ponds_leases$Authority)#3
unique(QLD_SLR_erosion_Freshwater_fish_ponds_leases$Authority)#4
unique(QLD_SLR_erosion_Hatchery_ponds_leases$Authority)#2
unique(QLD_SLR_erosion_Ornamental_ponds_leases$Authority)#1
unique(QLD_SLR_erosion_Marinefish_ponds_leases$Authority)#1

```
```{r}
#number of leases with ponds
unique(prawn_ponds_in_leases$qldglb_) #52
unique(Barramundi_ponds_in_leases$qldglb_) #42
unique(Redclaw_ponds_in_leases$qldglb_) #56
unique(Freshwater_fish_ponds_in_leases$qldglb_)#24
unique(Hatchery_ponds_in_leases$qldglb_)#6
unique(Ornamental_ponds_in_leases$qldglb_)#10
unique(Marine_fish_ponds_in_leases$qldglb_)#2
```


```{r}
#number of leases with exposed ponds 
unique(QLD_SLR_erosion_prawn_ponds_leases$qldglb_) #46
unique(QLD_SLR_erosion_Barramundi_ponds_leases$qldglb_)#16
unique(QLD_SLR_erosion_Redclaw_ponds_leases$qldglb_)#3
unique(QLD_SLR_erosion_Freshwater_fish_ponds_leases$qldglb_)#5
unique(QLD_SLR_erosion_Hatchery_ponds_leases$qldglb_)#2
unique(QLD_SLR_erosion_Ornamental_ponds_leases$qldglb_)#1
unique(QLD_SLR_erosion_Marinefish_ponds_leases$qldglb_)#2

```
```{r}
Final_species2024_leases_productive<-Final_species2024_leases%>%
  filter(Aqcltr_=="Y")
```

```{r}
difference_farms<- setdiff(QLD_ponds_in_leases$Authority, Final_species2024_leases_productive$Authority)
```

```{r}
difference_leases<- setdiff(QLD_ponds_in_leases$qldglb_, Final_species2024_leases_productive$qldglb_)
```

#multiple species
```{r}
prawn_barramundi_ponds<-prawn_ponds_in_leases%>%
  filter(grepl('Prawn/Barramundi', Species))
```
```{r}
sum(prawn_barramundi_ponds$pond_area_km2)
```
#multiple species
```{r}
prawn_redclaw_ponds<-prawn_ponds_in_leases%>%
  filter(grepl('Prawns/Redclaw', Species))
```
```{r}
sum(prawn_redclaw_ponds$pond_area_km2)
```
```{r}
barramundi_otherfish_ponds<-Barramundi_ponds_in_leases%>%
  filter(grepl('Barramundi/Freshwater fish', Species))
```
```{r}
sum(barramundi_otherfish_ponds$pond_area_km2)
```
```{r}
redclaw_freshwaterfish_ponds<-Redclaw_ponds_in_leases%>%
  filter(grepl('Freshwater fish', Species))
```
```{r}
sum(redclaw_freshwaterfish_ponds$pond_area_km2)
```
#saving multiple species results
```{r}
st_write(barramundi_otherfish_ponds, here("output_data/QLD_Aquaculture_distribution/RESULTS/QLD_pond_by_lease/multiple_species/barramundi_otherfish_ponds.gpkg"), delete_layer = TRUE)

st_write(redclaw_freshwaterfish_ponds, here("output_data/QLD_Aquaculture_distribution/RESULTS/QLD_pond_by_lease/multiple_species/redclaw_freshwaterfish_ponds.gpkg"), delete_layer = TRUE)

prawn_redclaw_ponds
st_write(prawn_redclaw_ponds, here("output_data/QLD_Aquaculture_distribution/RESULTS/QLD_pond_by_lease/multiple_species/prawn_redclaw_ponds.gpkg"), delete_layer = TRUE)

prawn_barramundi_ponds
st_write(prawn_barramundi_ponds, here("output_data/QLD_Aquaculture_distribution/RESULTS/QLD_pond_by_lease/multiple_species/prawn_barramundi_ponds.gpkg"), delete_layer = TRUE)

```

#checking which regions are expected to be more affected by SLR
```{r}
LGA<- st_read(here("raw_data/LGA/Local_Government_Areas.shp"))
```
```{r}
LGA_reproj<- st_transform(LGA, 3577)
```


```{r}
mostaffected_councils<- st_intersection(LGA_reproj, qld_leases_erosion)
```
```{r}
mostaffected_councils_km2<-mostaffected_councils%>%
   mutate(affected_area_km2 = affected_area_m2/1e6)
```


```{r}
# Sum values of affected_area_m2 for each city (LGA)
summed_data <- mostaffected_councils %>%
  group_by(LGA) %>%
  summarise(total_affected_area_m2 = sum(affected_area_m2, na.rm = TRUE))


# View the result
print(summed_data)
```
```{r}
# Rank LGAs by affected area
ranked_data <- mostaffected_councils %>%
  group_by(LGA) %>%
  summarise(total_affected_area_m2 = sum(affected_area_m2, na.rm = TRUE)) %>%
  arrange(desc(total_affected_area_m2)) %>%
  mutate(rank = row_number())
```

```{r}
# Sum values of affected_area_m2 for each city (LGA)
summed_data_km2 <- mostaffected_councils_km2 %>%
  group_by(LGA) %>%
  summarise(total_affected_area_km2 = sum(affected_area_km2, na.rm = TRUE))


# View the result
print(summed_data_km2)

```

```{r}
# Rank LGAs by affected area
ranked_data_km2 <- mostaffected_councils_km2 %>%
  group_by(LGA) %>%
  summarise(total_affected_area_km2 = sum(affected_area_km2, na.rm = TRUE)) %>%
  arrange(desc(total_affected_area_km2)) %>%
  mutate(rank = row_number())
```

```{r}
mostaffected_councils_km2<-mostaffected_councils_km2%>%
  mutate(propaffected_council= affected_area_km2/lease_area_km2)
```

```{r}
ranked_data_km2 <- mostaffected_councils_km2 %>%
 group_by(LGA) %>%
  summarise(
    total_affected_area_km2 = sum(affected_area_km2, na.rm = TRUE),
    propaffected_council = first(propaffected_council)  # LGA proprotion affected already calculated before
  ) %>%
  arrange(desc(total_affected_area_km2)) %>%
  mutate(rank = row_number())

# View the ranked result
print(ranked_data_km2)


```

```{r}
ranked_data <- mostaffected_councils %>%
 group_by(LGA) %>%
  summarise(
    total_affected_area_m2 = sum(affected_area_m2, na.rm = TRUE),
    propaffectedArea = first(propaffectedArea)  # Assuming values are consistent within each LGA
  ) %>%
  arrange(desc(total_affected_area_m2)) %>%
  mutate(rank = row_number())

# View the ranked result
print(ranked_data)


```
```{r}
# Load necessary libraries
library(ggplot2)
library(dplyr)

# Rank LGAs and prepare for plotting
ranked_data <- mostaffected_councils %>%
  group_by(LGA) %>%
  summarise(
    total_affected_area_m2 = sum(affected_area_m2, na.rm = TRUE),
    propaffectedArea = first(propaffectedArea)  # Assuming values are consistent within each LGA
  ) %>%
  arrange(desc(total_affected_area_m2)) %>%
  mutate(rank = row_number())

# Create a bar plot
ggplot(ranked_data, aes(x = reorder(LGA, -total_affected_area_m2), y = total_affected_area_m2)) +
  geom_bar(stat = "identity", fill = "darkblue") +
  coord_flip() +  # Flip the axis for better readability
  labs(x = "LGA", y = "Total Affected Area (m²) within Lots", title = "Ranked LGAs by Total Affected Area") +
  theme_minimal()

```



```{r}
# Load necessary libraries
library(sf)
library(ggplot2)

# Assuming you have an LGA shapefile or spatial object
# Load the LGA shapefile (adjust the file path accordingly)
#LGA<- st_read(here("raw_data/LGA/Local_Government_Areas.shp"))

# Join the ranked data with the shapefile data

ranked_df<-as.data.frame(ranked_data) %>%
  select(-geometry)
mapped_data <- LGA_reproj %>%
  full_join(ranked_df, by = "LGA")

# Plot the map
ggplot(mapped_data) +
  geom_sf(aes(fill = total_affected_area_m2*1e-6)) +
  scale_fill_viridis_c(option = "plasma", name = "Sea level \nrise exposure (km²)") +
   theme_minimal()

```
#inferno colour
```{r}
# Plot the map
ggplot(mapped_data) +
  geom_sf(aes(fill = total_affected_area_m2)) +
  scale_fill_viridis_c(option = "viridis", name = "Affected Area (m²)") +
  labs(title = "Ranking of LGAs by Total Exposed Aquaculture Area") +
  theme_minimal()

```
#plasma colour
```{r}
# Join the ranked data with the shapefile data

ranked_df_km2<-as.data.frame(ranked_data_km2) %>%
  select(-geometry)
mapped_data_km2 <- LGA_reproj %>%
  full_join(ranked_df_km2, by = "LGA")

# Plot the map
ggplot(mapped_data_km2) +
  geom_sf(aes(fill = total_affected_area_km2)) +
  scale_fill_viridis_c(option = "plasma", , name = "Sea level \nrise exposure (km²)", na.value = "lightgrey") +
   theme_minimal()
```


```{r}
library(ggrepel)
```
#ggrepel


```{r}

sub<-mapped_data %>%
    filter(is.na(total_affected_area_m2) == F,
           propaffectedArea>0.8)

# Calculate centroids for each LGA (for label positioning)
mapped_data_centroids <- sub %>%
  mutate(centroid = st_centroid(geometry)) %>%
  st_as_sf()

# Extract the coordinates of the centroids
centroid_coords <- st_coordinates(mapped_data_centroids$centroid)

# Convert the centroids to a data frame and add the LGA names
centroid_df <- data.frame(centroid_coords, LGA= sub$LGA)

# Plot the map with LGA names
ggplot(mapped_data) +
 geom_sf(aes(fill = total_affected_area_m2)) +
  scale_fill_viridis_c(option = "plasma", name = "Sea level \nrise exposure (m²)", na.value = "lightgrey") +
      theme_minimal() +  # Minimal theme
  geom_text_repel(data = centroid_df, aes(X, Y, label = LGA), size = 2, color = "black", max.overlaps = Inf)  # Add LGA names

```
```{r}

sub2<-mapped_data_km2 %>%
    filter(is.na(total_affected_area_km2) == F,
           propaffected_council>0.1)

# Calculate centroids for each LGA (for label positioning)
mapped_data_centroids <- sub2 %>%
  mutate(centroid = st_centroid(geometry)) %>%
  st_as_sf()

# Extract the coordinates of the centroids
centroid_coords <- st_coordinates(mapped_data_centroids$centroid)

# Convert the centroids to a data frame and add the LGA names
centroid_df <- data.frame(centroid_coords, LGA= sub2$LGA)

# Plot the map with LGA names
ggplot(mapped_data_km2) +
 geom_sf(aes(fill = total_affected_area_km2)) +
  scale_fill_viridis_c(option = "plasma", name = "Sea level \nrise exposure (km²)", na.value = "lightgrey") +
      theme_minimal() +  # Minimal theme
  geom_text_repel(data = centroid_df, aes(X, Y, label = LGA), size = 2, color = "black", max.overlaps = Inf)  # Add LGA names

```
#all LGAs all aquaculture final bar plot
#all leases plasma bar plot
```{r}
# Create a bar plot
ggplot(ranked_data_km2, aes(x = reorder(LGA, -total_affected_area_km2), y = total_affected_area_km2,  fill = propaffected_council)) +
  geom_bar(stat = "identity") +
  coord_flip() +  # Flip the axis for better readability
  labs(x = "LGA", y = "Total Exposed Area (km²) within Lots", title = "Ranked LGAs by Total Exposed Area") +
   scale_fill_viridis_c(option = "plasma", name = "Proportion of Exposed\n area by lot") +
  theme_minimal()

```
```{r}
# Create a bubble plot
ggplot(ranked_data, aes(x = rank, y = total_affected_area_m2, size = total_affected_area_m2, label = LGA)) +
  geom_point(alpha = 0.6, color = "blue") +
  geom_text(vjust = 1.5, hjust = 0.5) +
  labs(x = "Rank", y = "Total Affected Area (m²)", title = "Bubble Plot of LGAs by Affected Area") +
  theme_minimal() +
  scale_size_continuous(name = "Affected Area (m²)")
```
  
##most exposed LGAs for prawn
```{r}
mostaffected_LGA_Prawn<- st_intersection(LGA_reproj, QLD_SLR_erosion_prawn_ponds_leases)
```

```{r}
mostaffected_LGA_Prawn_km2<-mostaffected_LGA_Prawn%>%
  mutate(propaffected_prawn= affected_area_km2/pond_area_km2)
```

  
  
```{r}
# Sum values of affected_area_m2 for each city (LGA)
summed_data_prawn <- mostaffected_LGA_Prawn_km2 %>%
  group_by(LGA) %>%
  summarise(total_affected_area_km2 = sum(affected_area_km2, na.rm = TRUE))

# View the result
print(summed_data_prawn)
```
```{r}
# Rank LGAs by affected area
ranked_data_prawn <-  mostaffected_LGA_Prawn_km2 %>%
   group_by(LGA) %>%
  summarise(
    total_affected_area_km2 = sum(affected_area_km2, na.rm = TRUE),
    propaffected_prawn = first(propaffected_prawn)  # considered summing all values in the LGA
  ) %>%
  arrange(desc(total_affected_area_km2)) %>%
  mutate(rank = row_number())

# View the ranked result
print(ranked_data_prawn)

```
```{r}
# Rank LGAs and prepare for plotting
ranked_data_prawn <-  mostaffected_LGA_Prawn_km2 %>%
   group_by(LGA) %>%
  summarise(
    total_affected_area_m2 = sum(affected_area_m2, na.rm = TRUE),
    propaffected_prawn = first(propaffected_prawn)  # considered summing all values in the LGA
  ) %>%
  arrange(desc(total_affected_area_m2)) %>%
  mutate(rank = row_number())

# Create a bar plot
ggplot(ranked_data_prawn, aes(x = reorder(LGA, -total_affected_area_m2), y = total_affected_area_m2)) +
  geom_bar(stat = "identity", fill = "darkblue") +
  coord_flip() +  # Flip the axis for better readability
  labs(x = "LGA", y = "Total exposed pond Area (m²) ", title = "Ranked LGAs by prawn pond Area") +
  theme_minimal()

```

```{r}
# Join the ranked data with the shapefile data
mapped_data_prawn<- LGA_reproj %>%
  st_join(ranked_data_prawn, by = "LGA")

# Plot the map
ggplot(mapped_data_prawn) +
  geom_sf(aes(fill = total_affected_area_km2)) +
  scale_fill_viridis_c(option = "plasma", name = "Exposed Area (m²) ") +
  labs(title = "Ranking of LGAs by Total Exposed Prawn Ponds") +
  theme_minimal()

```

```{r}
# Calculate centroids for each LGA (for label positioning)
mapped_data_centroids <- mapped_data_prawn %>%
  mutate(centroid = st_centroid(geometry)) %>%
  st_as_sf()

# Extract the coordinates of the centroids
centroid_coords <- st_coordinates(mapped_data_centroids$centroid)

# Convert the centroids to a data frame and add the LGA names
centroid_df <- data.frame(centroid_coords, LGA= mapped_data_prawn$LGA.x)

# Plot the map with LGA names
ggplot(mapped_data_prawn) +
  geom_sf(aes(fill = total_affected_area_km2)) +  # Fill based on affected area
  scale_fill_viridis_c(option = "plasma", name = "Exposed Area (km²)") +  # Color scale
  labs(title = "Ranking of LGAs by Exposed prawn ponds area") +  # Title
  theme_minimal() #+  # Minimal theme
  #geom_text(data = centroid_df, aes(X, Y, label = LGA), size = 0.8, color = "black")  # Add LGA names

```

#most exposed LGAs for Barramundi
```{r}
mostaffected_LGA_Barramundi<- st_intersection(LGA_reproj, QLD_SLR_erosion_Barramundi_ponds_leases)
```
```{r}
mostaffected_LGA_Barramundi_km2<-mostaffected_LGA_Barramundi%>%
  mutate(propaffected_barra= affected_area_km2/pond_area_km2)
```

```{r}
# Sum values of affected_area_m2 for each city (LGA)
summed_data_Barramundi <- mostaffected_LGA_Barramundi_km2 %>%
  group_by(LGA) %>%
  summarise(total_affected_area_km2 = sum(affected_area_km2, na.rm = TRUE))

# View the result
print(summed_data_Barramundi)
```
```{r}
# Rank LGAs by affected area
ranked_data_Barramundi <-  mostaffected_LGA_Barramundi_km2 %>%
  group_by(LGA) %>%
  summarise(total_affected_area_km2 = sum(affected_area_km2, na.rm = TRUE)) %>%
  arrange(desc(total_affected_area_km2)) %>%
  mutate(rank = row_number())

# View the ranked result
print(ranked_data_Barramundi)

```
```{r}
# Join the ranked data with the shapefile data
mapped_data_Barramundi<- LGA_reproj %>%
  st_join(ranked_data_Barramundi, by = "LGA")

# Plot the map
ggplot(mapped_data_Barramundi) +
  geom_sf(aes(fill = total_affected_area_km2)) +
  scale_fill_viridis_c(option = "plasma", name = "Exposed Area (km²)") +
  labs(title = "Ranking of LGAs by Total Exposed Barramundi Ponds") +
  theme_minimal()

```

```{r}
ranked_data_Barramundi <- mostaffected_LGA_Barramundi_km2 %>%
  group_by(LGA) %>%
  summarise(
    total_affected_area_km2 = sum(affected_area_km2, na.rm = TRUE),
    propaffected_barra = first(propaffected_barra)  # considered summing all values in the LGA
  ) %>%
  arrange(desc(total_affected_area_km2)) %>%
  mutate(rank = row_number())

```


```{r}
# Create a bar plot
ggplot(ranked_data_Barramundi, aes(x = reorder(LGA, -total_affected_area_m2), y = total_affected_area_m2)) +
  geom_bar(stat = "identity", fill = "darkblue") +
  coord_flip() +  # Flip the axis for better readability
  labs(x = "LGA", y = "Total exposed Barramundi pond Area (m²) ", title = "Ranked LGAs by Barramundi pond Area exposed") +
  theme_minimal()

```

```{r}
# Calculate centroids for each LGA (for label positioning)
mapped_data_centroids <- mapped_data_Barramundi %>%
  mutate(centroid = st_centroid(geometry)) %>%
  st_as_sf()

# Extract the coordinates of the centroids
centroid_coords <- st_coordinates(mapped_data_centroids$centroid)

# Convert the centroids to a data frame and add the LGA names
centroid_df <- data.frame(centroid_coords, LGA= mapped_data_Barramundi$LGA.x)

# Plot the map with LGA names
ggplot(mapped_data_Barramundi) +
  geom_sf(aes(fill = total_affected_area_m2)) +  # Fill based on affected area
  scale_fill_viridis_c(option = "plasma", name = "Affected Area (m²)") +  # Color scale
  labs(title = "Ranking of LGAs by Exposed Barramundi ponds area") +  # Title
  theme_minimal() +  # Minimal theme
  geom_text(data = centroid_df, aes(X, Y, label = LGA), size = 0.8, color = "black")  # Add LGA names

```

#changing the bar plots to plasma 

```{r}
ggplot(ranked_data_prawn, aes(x = reorder(LGA, -total_affected_area_m2), y = total_affected_area_m2, fill = total_affected_area_m2)) +
  geom_bar(stat = "identity") +
  coord_flip() +  # Flip the axis for better readability
  labs(x = "LGA", y = "Total exposed pond Area (m²)", title = "Ranked LGAs by prawn pond Area") +
  scale_fill_viridis_c(option = "plasma") +
  theme_minimal()
```

```{r}
ggplot(ranked_data_prawn_km2, aes(x = reorder(LGA, -total_affected_area_km2), y = total_affected_area_km2, fill = propaffected_prawn)) +
  geom_bar(stat = "identity") +
  coord_flip() +  # Flip the axis 
  labs(x = "LGA", y = "Total exposed pond Area (km²)", title = "Ranked LGAs by prawn pond Area") +
  scale_fill_viridis_c(option = "plasma", name= " Proportion of ponds Exposed") +
  theme_minimal()
```

#Barramundi by total affected area by LGA
```{r}
# Create a bar plot
ggplot(ranked_data_Barramundi, aes(x = reorder(LGA, -total_affected_area_km2), y = total_affected_area_km2, , fill = total_affected_area_m2)) +
  geom_bar(stat = "identity") +
  coord_flip() +  # Flip the axis for better readability
  labs(x = "LGA", y = "Total exposed Barramundi pond Area (m²) ", title = "Ranked LGAs by Barramundi pond Area exposed") +
  scale_fill_viridis_c(option = "plasma") +
  theme_minimal()

```

#Barramundi by proportion of affected area by LGA
```{r}
# Create a bar plot
ggplot(ranked_data_Barramundi, aes(x = reorder(LGA, -total_affected_area_km2), y = total_affected_area_km2,  fill = propaffected_barra)) +
  geom_bar(stat = "identity") +
  coord_flip() +  # Flip the axis for better readability
  labs(x = "LGA", y = "Total exposed Barramundi pond Area (km²) ", title = "Ranked LGAs by Barramundi pond Area exposed") +
  scale_fill_viridis_c(option = "plasma", name= " Proportion of ponds Exposed") +
  theme_minimal()

```


#all leases plasma bar plot
```{r}
# Create a bar plot
ggplot(ranked_data, aes(x = reorder(LGA, -total_affected_area_m2), y = total_affected_area_m2, , fill = total_affected_area_m2)) +
  geom_bar(stat = "identity") +
  coord_flip() +  # Flip the axis for better readability
  labs(x = "LGA", y = "Total Affected Area (m²) within Lots", title = "Ranked LGAs by Total Affected Area") +
   scale_fill_viridis_c(option = "plasma") +
  theme_minimal()

```
#PropaffectedArea



#find the leases without ponds
```{r}
Leases_without_ponds<- setdiff(Final_species2024_leases$qldglb_, QLD_ponds_in_leases$qldglb_)
```

#creating the leases without ponds dataset
```{r}

# Assuming Final_species2024_leases is an sf object with geometries

# Filter the Final_species2024_leases dataset for rows with qldglb_ in Leases_without_ponds
spatial_leases_without_ponds <- Final_species2024_leases %>%
  filter(qldglb_ %in% Leases_without_ponds)

# Now spatial_leases_without_ponds contains the geometries and other data for leases without ponds

```
```{r}
st_write(spatial_leases_without_ponds, here("output_data/RESULTS/spatial_leases_without_ponds.gpkg"),delete_layer = TRUE)
```
#creating the ponds with leases dataset
```{r}
leases_with_ponds<-intersect(Final_species2024_leases$qldglb_, QLD_ponds_in_leases$qldglb_)
```
```{r}
spatial_leases_with_ponds <- Final_species2024_leases %>%
  filter(qldglb_ %in% leases_with_ponds)
```
```{r}
st_write(spatial_leases_with_ponds, here("output_data/RESULTS/spatial_leases_with_ponds.gpkg"),delete_layer = TRUE)
```
```{r}
leases_and_ponds<- st_union(spatial_leases_with_ponds, QLD_ponds_in_leases)
```
#saving the leases and ponds dataset
```{r}
st_write(leases_and_ponds, here("output_data/RESULTS/leases_and_ponds.gpkg"),delete_layer = TRUE)
```
#mapping the ponds and the leases 
```{r}
tmap_mode("view")+
tm_shape(spatial_leases_with_ponds)+
tm_polygons(col="red", alpha= 0.5)+
  tm_shape(QLD_ponds_in_leases)+
  tm_polygons(col="blue", alpha=0.8)
```
```{r}
QLD_ponds_in_leases_valid<-st_make_valid(QLD_ponds_in_leases)
```

```{r}
tmap_options(check.and.fix = TRUE)
```

#mapping more
```{r}
tmap_mode("view")+
tm_shape(QLD_ponds_in_leases_valid)+
tm_polygons(col="blue", alpha= 0.3)
```


#productivity scenarios and impact analysis 
#PRAWN
```{r}
# First, get the productivity scenarios
prawn_productivity <- calculate_productivity()

# Calculate impact on production for each scenario
impact_analysis <- data.frame(
  scenario = prawn_productivity$scenario,
  tonnes_per_km2 = prawn_productivity$tonnes_per_km2,
  total_area_km2 = sum(prawn_ponds_in_leases$pond_area_km2),
  affected_area_km2 = sum(QLD_SLR_erosion_prawn_ponds_leases_75$worst),
  current_potential_production = prawn_productivity$tonnes_per_km2 * sum(prawn_ponds_in_leases$pond_area_km2),
  production_loss = prawn_productivity$tonnes_per_km2 * sum(QLD_SLR_erosion_prawn_ponds_leases_75$worst),
  remaining_production = prawn_productivity$tonnes_per_km2 * (sum(prawn_ponds_in_leases$pond_area_km2) - sum(QLD_SLR_erosion_prawn_ponds_leases_75$worst))
)

# Add percentage loss
impact_analysis$percent_loss <- (impact_analysis$production_loss / impact_analysis$current_potential_production) * 100

# Save the results
write.csv(impact_analysis, 
          here("output_data/RESULTS/prawn_productivity_impact_analysis.csv"), 
          row.names = FALSE)
```
```{r}
# First, get the barramundi productivity scenarios
barramundi_productivity <- calculate_barramundi_productivity()

# Calculate impact on production for each scenario
barramundi_impact_analysis <- data.frame(
  scenario = barramundi_productivity$scenario,
  tonnes_per_km2 = barramundi_productivity$tonnes_per_km2,
  total_area_km2 = sum(Barramundi_ponds_in_leases$pond_area_km2),
  affected_area_km2 = sum(QLD_SLR_erosion_Barramundi_ponds_leases_15$worst),
  current_potential_production = barramundi_productivity$tonnes_per_km2 * sum(Barramundi_ponds_in_leases$pond_area_km2),
  production_loss = barramundi_productivity$tonnes_per_km2 * sum(QLD_SLR_erosion_Barramundi_ponds_leases_15$worst),
  remaining_production = barramundi_productivity$tonnes_per_km2 * (sum(Barramundi_ponds_in_leases$pond_area_km2) - sum(QLD_SLR_erosion_Barramundi_ponds_leases_15$worst))
)

# Add percentage loss
barramundi_impact_analysis$percent_loss <- (barramundi_impact_analysis$production_loss / barramundi_impact_analysis$current_potential_production) * 100

# Save the results
write.csv(barramundi_impact_analysis, 
          here("output_data/RESULTS/barramundi_productivity_impact_analysis.csv"), 
          row.names = FALSE)

# If you want to save both analyses in one Excel file
library(writexl)
impact_analyses <- list(
  Prawn = impact_analysis,
  Barramundi = barramundi_impact_analysis
)

write_xlsx(impact_analyses, 
           here("output_data/RESULTS/aquaculture_productivity_impact_analyses.xlsx"))
```

