---
title: "terra_GEE raster to polygons loop"
output: html_document
date: "2024-02-27"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#https://rspatial.github.io/terra/reference/terra-package.html

```{r}
library(terra)
library(rgdal)
library(raster)
library(sf)
library(tidyverse)
library(here)
library(tmap)
library(ggplot2)
library(tidyterra)
library(leaflet)
library(tmaptools)
library(dplyr)
```


#making the file list to loop all of them 
```{r}
gee_files<-list.files(here("GEE_data"), pattern = "s2_metrics", full.names = TRUE)

gee_files2<-gee_files[grep(gee_files, pattern = ".ovr")]
gee_files2b<-gee_files[grep(gee_files, pattern = ".aux.xml")]

gee_files3a<-gee_files[!gee_files %in% gee_files2b]
gee_files3<-gee_files3a[!gee_files3a %in% gee_files2]


```
#for loops 
#if you want to start in other number just redo from that on #i in number(where the is a 1 now) you want to start from (change back to 1 when finished to keep the code)
#if you want the 20th percentile then substitute the NDWI layer by : "NDWI_p20" 
```{r}

for(i in 1:length(gee_files3)){
  print(i)
  gee_geotiff<-terra::rast(gee_files3[[i]])
  NDWI_p80<- subset(gee_geotiff, "NDWI_p80")
  NDWI_p80[NDWI_p80 == 0]<-NA
  if(is.na(NDWI_p80@cpp$range_max) == TRUE){
  next
  }else{
  Poly_NDWI_p80 <- terra::as.polygons(NDWI_p80)
Poly_NDWI_p80_sf<-sf::st_as_sf(Poly_NDWI_p80) %>% 
  st_make_valid(.)
  num<-as.numeric(gsub(".*?([0-9]+).*", "\\1", gee_files3[[i]]))             
  s <- gee_files3[[i]]
 s1 <- unlist(strsplit(s, split='-', fixed=TRUE))
 num1<-s1[2]
 num2<-s1[3]
 test<-unlist(strsplit(num2, split='.', fixed=TRUE))
 num3<-test[1]
 
 
 st_write(Poly_NDWI_p80_sf, here(paste0("output_data/GEE_shp_20_21/NDWI_p80_",num1,"-",num3,".shp")), append = TRUE)

}
 
}


```

#in case you need to find one among others in the same file then do this , the last part of the path is the name of the file you are looking for
```{r}
#which(gee_files3 == here("GEE_data/s2_metrics_export_vizualization_bla-0000172800-0000110592.tif"))
```



#stick all the shapefiles from the GEE output 

#worked properly from here to combined
#call folder with files
```{r}
shp_files<-list.files(here("D:/Documents_HD/QLD_SLR_Aquaculture/output_data/GEE_shp_20_21"), pattern = "NDWI_p80", full.names = TRUE)
```

#separate in the folder the files with different endings that arent .shp
```{r}
shp_filesdbf<-shp_files[grep(shp_files, pattern = ".dbf")]
shp_filesprj<-shp_files[grep(shp_files, pattern = ".prj")]
shp_filesshx<-shp_files[grep(shp_files, pattern = ".shx")]
```

#make lists subtracting from those done above
```{r}
shp_fileswithoutdbf<-shp_files[!shp_files %in% shp_filesdbf]
shp_fileswithoutdbfprj<-shp_fileswithoutdbf[!shp_fileswithoutdbf %in% shp_filesprj]
shp_fileswithoutdbfprjshx<- shp_fileswithoutdbfprj[!shp_fileswithoutdbfprj %in% shp_filesshx]
```

#generate a list 
```{r}
shapes<-list()
```


#read all the shapefiles in a loop
```{r}
for (n in 1:length(shp_fileswithoutdbfprjshx)) {
  shapes[[n]] <- st_read(shp_fileswithoutdbfprjshx[n])}
 
if (length(shp_fileswithoutdbfprjshx) == 0) {
  stop("No shapefiles found in the folder.")
}
```
#combined all 37 shapefiles
```{r}
combined_shapefile <- bind_rows(shapes)
```

#save the combined shapefile
```{r}
st_write(combined_shapefile, here("output_data/QLD_aqua_ponds_combined_shapefile_NDWI_p80.shp"), delete_layer = TRUE)
```



